---
title: "Replication & Extension of Regional Favoritism (Hodler & Raschky, 2014)"
doc-type: "Seminar Paper"
course-info: "Applied Econometrics Using GIS Techniques · SoSe 2026"
lecturer: "Prof. Dr. Erkan Gören"
author:
  - name: Ömer Furkan Çoban
    email: oemer.furkan.coban@uni-oldenburg.de
    affiliations:
      - name: Carl von Ossietzky University of Oldenburg
        department: Applied Economics and Data Science
        city: Oldenburg
        country: Germany
date: "2026-09-15"
date-format: "DD MMMM YYYY"
abstract: |
  Hodler and Raschky (2014) find that a region grows brighter at night
  while it is the birth region of the sitting political leader, evidence
  of regional favoritism. This paper asks whether that finding survives
  being rebuilt rather than re-run: boundaries come from GADM rather
  than their CIESIN source, birthplaces from PLAD and a Wikidata
  supplement rather than their own geocoding, and light is extracted
  here from raw DMSP-OLS composites. On
  their exact 1992-2009 sample, seven of the eight columns of their
  Table II reproduce in sign and significance, with a birth-region
  coefficient of 0.032 against their 0.038, implying roughly one percent
  higher regional output per year of incumbency.
  Table IV's spatial pattern reproduces as well, fading one grid step
  sooner. Extending the panel to 2023 on a harmonized DMSP/VIIRS series
  strengthens the result: all seven extended specifications are
  significant and the coefficient rises to 0.048. It also recovers the
  one column that fails on the original window, the extensive margin,
  suggesting that null reflects the DMSP sensor's limits rather than a
  missing effect. Two discrepancies do not resolve: the population
  control enters with the opposite sign throughout, and the tightest
  spatial unit reverses their directional conclusion.
keywords:
  - Regional favoritism
  - Nighttime lights
  - Replication
  - Political economy
  - Geographic information systems
journal:
  name: Applied Econometrics Using GIS Techniques, seminar paper
bibliography: references.bib
csl: ../05_presentation/apa.csl
link-citations: true
execute:
  echo: false
  warning: false
  message: false
format:
  elsevier-pdf:
    keep-tex: true
    template-partials:
      - before-body.tex
    include-in-header:
      # tabularx gives stretchable X columns, used by Table 4 to fill the
      # text width without rescaling the font the way \resizebox would.
      #
      # The float parameters are relaxed so Figure 2 and Table 3, which
      # together occupy about 90% of a text block, can share one page.
      # LaTeX's defaults reserve at least 20% of every page for text
      # (\textfraction) and cap a page at two top floats, which forces
      # that pair apart no matter how they are ordered in the source.
      text: |
        \usepackage{tabularx}
        \usepackage{float}
        \renewcommand{\topfraction}{0.92}
        \renewcommand{\bottomfraction}{0.7}
        \renewcommand{\textfraction}{0.06}
        \renewcommand{\floatpagefraction}{0.85}
        \setcounter{topnumber}{3}
        \setcounter{totalnumber}{4}
    journal:
      formatting: preprint
      model: 3p
      cite-style: authoryear
  html:
    title: "Replication & Extension of Regional Favoritism"
    subtitle: "(Hodler & Raschky, 2014)"
    embed-resources: true
    theme: cosmo
    toc: true
    toc-depth: 2
    number-sections: true
    fig-width: 8
    format-links: false
    include-in-header:
      # Reuses the presentation's own three-typeface system and
      # navy/gold palette (see ../05_presentation/theme.scss) so the HTML
      # paper reads as the same project as the slide deck, rather than
      # a generic Bootstrap document. The four result tables' own
      # .ptbl-* markup (built inline in each table's HTML branch) is
      # styled here to match the presentation's .cmp-table look.
      text: |
        <link rel="stylesheet" href="https://fonts.googleapis.com/css2?family=Fraunces:opsz,wght@9..144,400;9..144,500;9..144,600;9..144,700&family=Source+Serif+4:opsz,wght@8..60,400;8..60,500;8..60,600&family=IBM+Plex+Mono:wght@400;500&display=swap">
        <style>
        :root{
          --paper:#fbf9f4; --paper-panel:#f3efe3; --ink:#24211c;
          --ink-soft:#6b6459; --ink-faint:#a29a89; --navy:#1d2f52;
          --navy-soft:#3a4d73; --gold:#a97e2f; --gold-soft:#e4d3a8;
          --rule:#e3dac2;
        }
        body{
          background:var(--paper); color:var(--ink);
          font-family:"Source Serif 4",Georgia,"Times New Roman",serif;
          font-size:17px; line-height:1.65;
        }
        h1,h2,h3,h4,h5,h6{
          font-family:"Fraunces",Georgia,serif; color:var(--navy);
          font-weight:600; letter-spacing:-0.01em;
        }
        h1.title{ font-weight:700; font-size:34px; }
        .subtitle, p.subtitle{ font-family:"Fraunces",Georgia,serif; font-style:normal; color:var(--navy); font-weight:600; font-size:34px; }
        .doc-type-label{
          font-family:"Fraunces",Georgia,serif; font-style:italic; font-size:1.15rem;
          letter-spacing:0.02em; color:var(--gold); font-weight:500; margin-top:0.5rem;
        }
        a{ color:var(--navy); }
        a:hover{ color:var(--gold); }
        code, pre, kbd, samp{ font-family:"IBM Plex Mono",ui-monospace,monospace; }
        pre{ background:var(--paper-panel); border:1px solid var(--rule); border-radius:4px; }
        blockquote{ border-left:3px solid var(--gold); background:var(--paper-panel); padding:0.6rem 1rem; color:var(--ink-soft); }
        hr{ border-color:var(--rule); }
        /* No color/font override on the container itself: it was
           cascading into the heading labels (making Published/Course/
           Semester/Lecturer a lighter grey than Author/Affiliation,
           which get their color from a more specific quarto rule this
           container-level one doesn't reach) and into the values.
           Targeting .quarto-title-meta-contents p directly instead
           matches Author/Affiliation's own value styling without
           touching the heading labels' color at all. */
        .quarto-title-block .quarto-title-meta-contents p{ font-family:"Source Serif 4",Georgia,"Times New Roman",serif; font-size:1rem; color:var(--ink); }
        .abstract{ background:var(--paper-panel); border:1px solid var(--rule); border-radius:6px; padding:1rem 1.25rem; }
        .abstract .block-title, div.abstract > .abstract-title{ font-family:"Fraunces",serif; color:var(--navy); font-weight:600; margin-top:0; }

        /* Quarto caps the content column at calc(850px - 3em) and the
           TOC track at minmax(75px,145px) no matter the viewport (see
           its own .page-columns grid) -- the 17-column result tables
           need more than that, so this widens both tracks for this
           document specifically rather than shrinking table type
           further. Redeclares the whole named-line grid (partial
           overrides aren't possible) for the one breakpoint/class
           combination this single-page document actually renders
           (body.quarto-light, no floating/docked/toc-left). */
        @media (min-width: 992px) {
          body .page-columns{
            display:grid; gap:0;
            grid-template-columns:
              [screen-start] 1.5em [screen-start-inset] 3fr
              [page-start page-start-inset] 35px [body-start-outset] 35px
              [body-start] 1.5em
              [body-content-start] minmax(500px, calc(1180px - 3em)) [body-content-end]
              1.5em [body-end] 35px [body-end-outset] minmax(140px, 220px)
              [page-end-inset] 35px [page-end] 3fr
              [screen-end-inset] 1.5em [screen-end];
          }
        }

        #TOC, nav[role="doc-toc"]{
          font-family:"Source Serif 4",Georgia,"Times New Roman",serif; font-size:0.88em;
          background:var(--paper-panel); border:1px solid var(--rule);
          border-radius:6px; padding:0.9rem 1rem;
        }
        #TOC #toc-title, nav[role="doc-toc"] #toc-title{
          font-family:"Fraunces",serif; font-weight:600; color:var(--navy);
          font-size:1.05rem; margin-bottom:0.5rem;
        }
        #TOC ul, nav[role="doc-toc"] ul{ padding-left:0; }
        /* Bootstrap's own .nav-link rule (color: the theme's link blue,
           font-weight 600) otherwise wins this: it's what every TOC
           item and the "PDF (elsevier)" link actually carry as a
           class, and it turned out more specific than the plain #TOC a
           selector above -- !important settles it instead of chasing
           specificity further. */
        #TOC a, #TOC a.nav-link, nav[role="doc-toc"] a{
          color:var(--ink-soft) !important; border-left:2px solid transparent;
          padding:0.15rem 0 0.15rem 0.6rem; display:block;
          font-weight:400 !important;
          transition:color .15s, border-color .15s;
        }
        #TOC a:hover, #TOC a.nav-link:hover, nav[role="doc-toc"] a:hover{
          color:var(--navy) !important; border-left-color:var(--gold-soft);
        }
        #TOC a.active, #TOC a.nav-link.active, nav[role="doc-toc"] a.active{
          color:var(--navy) !important; font-weight:600 !important; border-left-color:var(--gold);
        }
        /* "Other Formats" / PDF link: a sidebar-scoped h2 rule beats
           the page's general h1-h6 Fraunces rule, so this is restated
           with matching specificity rather than relying on that one. */
        #TOC .quarto-alternate-formats h2, #TOC .quarto-alternate-formats-title{
          font-family:"Fraunces",serif !important; font-weight:600; color:var(--navy);
          font-size:0.95rem; margin:1rem 0 0.4rem; text-transform:none;
        }
        #TOC .quarto-alternate-formats a{
          color:var(--ink-soft) !important; font-weight:400 !important;
          padding:0.15rem 0 0.15rem 0.6rem; border-left:2px solid transparent; display:block;
        }
        #TOC .quarto-alternate-formats a:hover{ color:var(--navy) !important; border-left-color:var(--gold-soft); }
        figcaption, .figure-caption{ font-style:italic; color:var(--ink-soft); font-size:0.9em; }

        /* Figures 1 and 2 are exported (SVG/PNG) on an opaque white
           canvas; multiply blends that white against the page's own
           near-white ground instead of showing a mismatched white box. */
        #fig-goh img, #fig-erdogan-units img{ mix-blend-mode:multiply; }

        /* Result tables (Table I/II/IV/Extension): Table I is a plain
           kableExtra table (Bootstrap classes only, styled generically
           below); the other three build their own .ptbl markup, styled
           to match the presentation's .cmp-table look. */
        table:not(.ptbl){ font-variant-numeric:tabular-nums; }
        table:not(.ptbl) thead th{ font-family:"Fraunces",serif; font-weight:600; color:var(--navy); border-bottom:1.5px solid var(--ink) !important; }
        /* Row labels (e.g. "NationalGDP_ct-1", "(country-year)") are
           short and should stay on one line rather than wrapping
           mid-word the way a narrow first column otherwise forces. */
        table:not(.ptbl) td:first-child, table:not(.ptbl) th:first-child{ white-space:nowrap; }

        /* Table II/IV/the extension table run to 14-17 columns; sized
           tight enough (vs. the presentation's own .cmp-table, built for
           a 1280px slide) to fit the content column's width without a
           horizontal scrollbar on a normal desktop viewport. overflow-x
           stays on as a fallback for narrower viewports rather than
           something this is meant to rely on. */
        .ptbl-wrap{ width:100%; overflow-x:auto; margin:1.25rem 0; }
        table.ptbl{ width:100%; border-collapse:collapse; font-size:0.78rem; font-variant-numeric:tabular-nums; background:transparent; }
        table.ptbl th, table.ptbl td{ padding:3px 5px; text-align:center; white-space:nowrap; }
        table.ptbl td:first-child, table.ptbl th:first-child{ text-align:left; white-space:nowrap; }
        table.ptbl thead tr:first-child th{ font-family:"Fraunces",serif; font-weight:600; color:var(--navy); border-bottom:none; padding-bottom:2px; }
        table.ptbl thead tr:last-child th{ font-weight:500; color:var(--ink-soft); font-size:0.78em; border-bottom:1.5px solid var(--ink); padding-top:2px; padding-bottom:5px; }
        table.ptbl tbody tr.ptbl-foot-first td{ border-top:1px solid var(--rule); padding-top:6px; }
        table.ptbl tbody tr:last-child td{ border-bottom:1.5px solid var(--ink); }
        table.ptbl .ptbl-shade{ background:var(--paper-panel); }
        table.ptbl .ptbl-se{ color:var(--ink-soft); font-size:0.88em; }
        table.ptbl .ptbl-sub{ color:var(--ink-soft); font-size:0.85em; padding-left:1.25em; }
        .ptbl-notes{ font-size:0.8rem; color:var(--ink-soft); margin-top:0.5rem; line-height:1.5; }
        </style>
    include-after-body:
      text: |
        <script>
        document.addEventListener("DOMContentLoaded", function () {
          // Every link that isn't a same-page anchor (a TOC entry, a
          // "Table 3"/"Section 5.1" cross-reference, a footnote) opens
          // in a new tab instead of navigating away from this document
          // -- citations, DOI/URL references, and the Other Links list.
          document.querySelectorAll("a[href]").forEach(function (a) {
            if (a.getAttribute("href").charAt(0) !== "#") {
              a.setAttribute("target", "_blank");
              a.setAttribute("rel", "noopener");
            }
          });
          var src = document.getElementById("extra-title-meta-source");
          if (src) {
            var groups = document.querySelectorAll(".quarto-title-meta");
            var target = null;
            groups.forEach(function (g) {
              if (g.textContent.indexOf("Published") !== -1) target = g;
            });
            if (target) {
              while (src.firstChild) target.appendChild(src.firstChild);
            }
            src.remove();
          }
          // Same move for the "Other Links" block. format-links:false
          // removes quarto's own "Other Formats" block entirely now, so
          // there's nothing to anchor after -- append straight into TOC.
          var linksSrc = document.getElementById("extra-toc-links-source");
          if (linksSrc) {
            var toc = document.getElementById("TOC");
            // Scoped to #TOC: an unscoped query also matches the (not
            // yet moved) .quarto-alternate-formats sitting inside this
            // very hidden source div wherever it rendered in the body,
            // which is a no-op move that then gets deleted below.
            var formats = toc ? toc.querySelector(".quarto-alternate-formats") : null;
            if (formats && formats.parentNode) {
              formats.parentNode.insertBefore(linksSrc.firstElementChild, formats.nextSibling);
            } else if (toc) {
              toc.appendChild(linksSrc.firstElementChild);
            }
            linksSrc.remove();
          }
          // The doc-type label ("Seminar Paper"/"Supplementary
          // Material") goes right after the title+subtitle, inside
          // quarto's own .quarto-title block, which has no YAML hook
          // for an extra line either.
          var typeSrc = document.getElementById("extra-doc-type-source");
          if (typeSrc) {
            var titleBlock = document.querySelector(".quarto-title");
            if (titleBlock) {
              titleBlock.appendChild(typeSrc.firstElementChild);
            }
            typeSrc.remove();
          }
        });
        </script>
---

```{r}
#| echo: false
#| results: asis
# Doc-type label ("Seminar Paper"), moved next to the title/subtitle by
# the include-after-body script -- same hidden-source + DOM-move
# technique as the blocks below, since quarto's title block has no YAML
# field for an extra line here either.
if (knitr::is_html_output()) {
    knitr::asis_output(paste0(
        '<div id="extra-doc-type-source" style="display:none">',
        '<p class="doc-type-label">Seminar Paper</p>',
        '</div>'
    ))
}
```

```{r}
#| echo: false
#| results: asis
# Hand-written raw HTML in plain markdown gets escaped by pandoc's
# stricter raw-block detection; asis_output() bypasses that the same
# way every result table in this document already does. This renders
# hidden, in body order, and a script (include-after-body, below) moves
# its three field-groups into the title block's own second
# .quarto-title-meta div (the one already holding "Published") so they
# sit in that same row rather than in a separate block of their own --
# quarto builds that title block straight from YAML with no hook to add
# fields to it directly, so this is a DOM move rather than a template
# edit.
if (knitr::is_html_output()) {
    knitr::asis_output(paste0(
        '<div id="extra-title-meta-source" style="display:none">',
        '<div><div class="quarto-title-meta-heading">Course</div>',
        '<div class="quarto-title-meta-contents"><p>Applied Econometrics Using GIS Techniques</p></div></div>',
        '<div><div class="quarto-title-meta-heading">Semester</div>',
        '<div class="quarto-title-meta-contents"><p>SoSe 2026</p></div></div>',
        '<div><div class="quarto-title-meta-heading">Lecturer</div>',
        '<div class="quarto-title-meta-contents"><p>Prof. Dr. Erkan Gören</p></div></div>',
        '</div>'
    ))
}
```

```{r}
#| echo: false
#| results: asis
# Same hidden-source + DOM-move technique as the title-meta block above,
# targeting quarto's "Other Formats" sidebar block this time. Paths are
# relative to paper.html's own location (04_paper/). "Paper (HTML)" is
# dropped from the list below since it's the current page -- linking a
# page to itself in its own "other links" list is a no-op that only
# invites confusion; supplementary.qmd's own version of this chunk
# drops "Supplementary (HTML)" for the same reason.
if (knitr::is_html_output()) {
    links <- list(
        list(href = "paper.html", icon = "bi-filetype-html", label = "Paper (HTML)"),
        list(href = "paper.pdf", icon = "bi-file-pdf", label = "Paper (PDF)"),
        list(href = "supplementary.html", icon = "bi-filetype-html", label = "Supplementary (HTML)"),
        list(href = "supplementary.pdf", icon = "bi-file-pdf", label = "Supplementary (PDF)"),
        list(href = "../05_presentation/index.html", icon = "bi-easel2", label = "Presentation (slides)"),
        list(href = "../05_presentation/Coban_RegionalFavoritism.pdf", icon = "bi-file-pdf", label = "Presentation (PDF)"),
        list(href = "https://github.com/ofurkancoban/Regional_Favoritism_Replication", icon = "bi-box-seam", label = "Replication Package")
    )
    links <- Filter(function(l) l$href != "paper.html", links)
    items <- vapply(links, function(l) {
        sprintf(
            '<li><a href="%s"><i class="bi %s"></i>%s</a></li>',
            l$href, l$icon, l$label
        )
    }, character(1))
    knitr::asis_output(paste0(
        '<div id="extra-toc-links-source" style="display:none">',
        # A real <h2> here gets picked up by quarto's anchorjs script,
        # which scans the whole document for headings and injects an
        # anchor-link icon into each one -- harmless on real section
        # headings, but it visibly broke this sidebar label's spacing
        # since anchorjs has no reason to expect a heading down here.
        # A <p> styled to look identical avoids it being a heading at all.
        '<div class="quarto-alternate-formats"><p class="quarto-alternate-formats-title">Other Links</p><ul>',
        paste(items, collapse = ""),
        '</ul></div>',
        '</div>'
    ))
}
```

<!--
Section budget (~12-13 pages body, 15-page hard cap excl. appendix):
  1 Introduction              ~1-1.5p
  2 Literature                ~0.5-1p
  3 Data                      ~2p
  4 Empirical Framework       ~1p
  5 Results                   ~4-5p (Table II + Table IV)
  6 Discussion/Limitations    ~1-1.5p
  7 Conclusion                ~1p
Everything not needed to support Table II/IV goes to supplementary.qmd instead.
-->

# Introduction {#sec-introduction}

A political leader's home region gets measurably brighter at night, in
satellite-recorded nighttime light data, while that leader holds power.
This is the central empirical claim of @hodler2014, and it is a claim
about a specific, testable channel of political favoritism: leaders
steer public resources toward the region where they were born, not
necessarily toward the region that needs them most.

Testing this directly with government spending data is difficult, and
not by coincidence. Fiscal records at the subnational level are missing
or unreliable in exactly the settings where regional favoritism is most
likely to occur, in weak-institution states with limited budget
transparency, so the evidence would be censored precisely where the
effect is largest. Nighttime light intensity, measured by satellite,
offers a way around this. It is recorded by the same instrument and the
same method everywhere, it exists for every populated region regardless
of what any government chooses to publish, and no domestic authority can
edit or suppress it. It is, in short, an outcome a government cannot
manipulate even if it wanted to, which makes it a credible proxy for
local economic activity and infrastructure investment [@henderson2012].

@hodler2014 build on this logic with a global panel of 38,427
subnational regions across 126 countries, observed annually from 1992 to
2009, and estimate that a region becomes on average about four percent
brighter while it is the birth region of the sitting political leader.
The effect is strongest where institutions are weak and education is
low, and it grows with the availability of foreign aid and oil rents,
consistent with a story in which favoritism requires both a motive and
the means to act on it.

What that average effect looks like in a single case is shown in
@fig-goh. Gôh, a region in central Ivory Coast, tracked the national
average closely throughout the 1990s, then diverged sharply in 2000,
the year Laurent Gbagbo, born in Gôh, took office as president: the
region pulled away from the national trend and kept climbing over the
following years, while the rest of the country stayed flat. The
satellite images tell the same story spatially, with the lit area
inside the region's boundary thickening between 1996 and 2009. One
region is of course not evidence on its own, and Gôh was selected
precisely because it is a clear case; the point of the figure is to
make concrete what the estimates in the rest of the paper measure on
average across thousands of regions.

::: {.content-visible when-format="pdf"}
![DMSP-OLS stable lights over Gôh, Ivory Coast, at four points in time,
and the region's nighttime light trend against the national average,
1992-2013. Laurent Gbagbo, born in Gôh, took office in
2000.](img/goh_combined_paper.pdf){#fig-goh width=95%}
:::

::: {.content-visible when-format="html"}
![DMSP-OLS stable lights over Gôh, Ivory Coast, at four points in time,
and the region's nighttime light trend against the national average,
1992-2013. Laurent Gbagbo, born in Gôh, took office in
2000.](img/goh_combined_paper.svg){#fig-goh width=95%}
:::

This paper's contribution has three components: a replication of Table
II, the main results and robustness battery; a replication of Table IV,
the test of how the effect varies with the size of the geographic unit
used to measure it; and an extension of the panel well beyond HR's
original 1992-2009 window. The replication is
built on an independently constructed pipeline: the region-leader
crosswalk, the birthplace coordinates, and the grid-cell geometry used
for the geographic-extent test were all built from raw sources rather
than reused from any existing processed panel. The headline finding
survives this independent reconstruction. Seven of the eight Leader
coefficients in Table II replicate in sign and statistical
significance, and Table IV's central pattern, that the effect shrinks
steadily as the geographic unit of measurement grows larger and
eventually becomes indistinguishable from zero, replicates as well,
though the point at which it stops clearing conventional significance
falls one grid step earlier here than in the authors' own data.
@sec-results-table2 reports the one Table II column that does not
replicate, and @sec-discussion collects that alongside the paper's
other departures from the original. The extension, built on a
harmonized DMSP/VIIRS nighttime-lights panel running through 2023 and
an independently constructed population pipeline, asks whether the
same effect holds over a substantially longer horizon than HR
originally had available. It does, and it is larger rather than
smaller: the birth-region coefficient rises from 0.032 on the
replication window to 0.048 over 1992-2023, and the one specification
that fails to replicate in the shorter window recovers once the more
sensitive VIIRS sensor enters the series, which is reported in
@sec-extension. Five
additional HR tables the project replicated but that do not fit within
this paper's scope are reported separately in the Supplementary
Materials.

# Literature {#sec-literature}

Regional favoritism sits within a broader literature on distributive
politics, the study of how governments allocate resources across
constituencies for political rather than purely economic reasons. Prior
to @hodler2014, this literature had relied almost entirely on
single-country spending data [@golden2013], leaving systematic,
cross-country evidence of favoritism largely absent, in part because
subnational fiscal records are themselves missing or unreliable in the
settings where favoritism is most likely. Within that literature, a
specific strand asks whether leaders favor the group or place they come
from. @franck2012 show that in Sub-Saharan Africa, districts sharing
the president's ethnicity see better educational and health outcomes
while that president is in power, evidence of ethnic rather than
strictly regional favoritism. @hodler2014 ask the related but distinct
question of whether favoritism attaches to a leader's birth *region*,
defined administratively rather than ethnically, and whether it is
visible in a measure of economic activity rather than in
public-service outcomes.

That measure is nighttime light intensity, whose use as a proxy for
subnational economic activity is itself a distinct methodological
contribution. @henderson2012 establish that satellite-recorded light is
informative about output growth even where official statistics are
weak or absent, precisely the setting in which government spending
data cannot be trusted to reveal favoritism directly. @hodler2014's
contribution is to combine this measurement tool with a global,
leader-birthplace dataset [@goemans2009] and a within-country,
within-year identification strategy, allowing regional favoritism to
be tested at a scale and with a design no single-country study of
distributive politics could match. More recently, @bora2025 extend this
approach into the higher-frequency VIIRS era and find that the effect
appears immediately upon a leader taking office rather than with a lag,
with a further premium during the COVID-19 pandemic concentrated in
weaker democracies, a modern-era pattern this paper's own extended
window speaks to directly.

Against this backdrop, what this paper adds is less a new claim than a
stress test of an existing one. Building the crosswalk, birthplace
coordinates, and geometry independently, rather than reusing HR's own
processed panel, is what makes the result informative about how robust
the finding is to reasonable implementation choices, not just about
whether it replicates. Reporting where it does not fully hold up
alongside where it does serves the same end: a literature's confidence
in a finding should rest on a complete account of the evidence, not
only the parts that confirm it.

# Data {#sec-data}

## Outcome: Nighttime Light Intensity {#sec-outcome}

The dependent variable is DMSP-OLS stable lights [@noaa-dmsp], the
same series the authors use. The raw signal comes from the Operational
Linescan System carried on US Air Force Defense Meteorological
Satellite Program satellites, a low-light sensor designed to image
moonlit cloud cover at night that also happens to pick up artificial
lighting on the ground. NOAA's National Geophysical Data Center turns
the raw passes into annual composites at 30 arc-second resolution
(about 1 km at the equator), reporting a digital number from 0 to 63
for each grid cell. The stable-lights product used here is the
cleaned version of that composite: cloud-contaminated observations are
dropped, and ephemeral light sources, gas flares, fires, and other
transient events, are filtered out by keeping only lights that appear
consistently across the year, using NOAA's own noise-floor thresholds
for areas expected to be free of detectable light [@baugh2010], the
same cleaning step the authors rely on. This is what makes the series
suitable for measuring persistent infrastructure like electrification
rather than one-off events. In years covered by two DMSP satellites, most of
the panel, this project pixel-averages the two composites before
extraction, matching the authors' own convention of an annual
composited mean across satellites; the country-year fixed effects
described in @sec-empirical absorb any residual cross-satellite jump
this leaves. Region-year values are the average digital number
over each region's area. Following the authors, every specification uses the
log of light intensity plus a small constant, $\ln(\text{Light}_{ict}
+ 0.01)$, rather than the raw level. The constant is necessary because
a large share of region-years, mostly rural areas with little or no
artificial lighting, record a light value of exactly zero, and the log
of zero is undefined; adding 0.01 before taking logs keeps those unlit
region-years in the estimation sample instead of dropping them, at the
cost of a mechanical floor on the transformed variable that has no
substantive interpretation of its own. The authors report an analogous
concentration in their own panel, 10.27% of observations at the lower
bound and a further 0.85% at the sensor's upper bound of 63, and cite
the same log(+0.01) convention used here, following both @henderson2012
and @michalopoulos2013 [see also @michalopoulos2014]. This paper's own
panel concentrates somewhat less at both ends, 9.18% at zero and 0.36%
at the ceiling, consistent with a different boundary source placing
somewhat fewer regions in either extreme rather than any difference in
method.

## Leader Birthplace {#sec-leader-birthplace}

Each leader's identity and tenure dates come from Archigos
[@goemans2009], a cross-national dataset that records who ruled each
country and over what dates; the authors use the same source for the
same purpose. Archigos does not record every leader's birthplace, so
this project supplements it with the Political Leaders' Affiliation
Database [@plad2024] and, for leaders still missing after that merge,
a manual Wikidata/Wikipedia scrape [@wikidata-supplement]. Following
the authors, leaders recorded as born outside the country they led are
excluded from the `Leader` regressor rather than assigned a foreign
birth region; the authors report that the leaders their own approach
drops for missing birthplace information were, without exception but
one, in office under 50 days (p. 1006, fn. 11), which is why that kind
of exclusion is unlikely to matter much in either panel. The authors'
own birthplace-to-region match works differently from this
replication's: they geocode via CIESIN's settlement-point shapefiles
where a birth settlement can be identified, falling back to raw
birthplace coordinates otherwise (p. 1006), whereas this project takes
PLAD's own already-geocoded region assignment directly, supplemented
by the Wikidata coordinates described above. Of the 919
Archigos leader-spells overlapping this paper's full 1992-2013 panel
window (wider than the authors' own 1992-2009 window, since this
paper's underlying panel extends further, as @sec-extension uses),
PLAD supplies a birthplace for 799 (86.9%); the Wikidata supplement
resolves a further 33, bringing total coverage to 832 spells (90.5%).
The remaining 87 spells (9.5%) stay uncovered, mostly leaders from 25
countries PLAD has no entry for at all, and are excluded from the
`Leader` regressor rather than imputed. The regressor itself, `Leader`, is entered with
a one-year lag rather than contemporaneously. The lag serves two
purposes. First, a leader can take office at any point within a
calendar year, so the contemporaneous year's light reading is only
partly observed under that leader; lagging one year guarantees the
region was governed by the same leader for the entire period being
measured. Second, favoritism plausibly operates through channels, such
as infrastructure spending or electrification projects, that take time
to build and are unlikely to be visible from space within the same
year a leader takes office.

## Geometry and Sample {#sec-geometry}

The authors' subnational regions come from CIESIN [@ciesin-subadbnd]
(the Center for International Earth Science Information Network at
Columbia University) and its project partners, at the second
administrative level, and are not publicly redistributed as a
standalone boundary file. This replication uses GADM 3.6 [@gadm36]
instead, at every level of aggregation: the ADM2-level regions used
for the main results and the ADM1-level geometry used in the
geographic-extent test, both the full region and the hole-punched
version with the leader's home district cut out, are all built from
the same GADM 3.6 vintage, so no crosswalk between geometry sources
is needed anywhere in this replication. GADM 3.6 is not a
reconstruction of the authors' own CIESIN boundaries, which is a
source of divergence between the two panels discussed further in
@sec-discussion. The estimation sample throughout the
paper is restricted to the authors' exact set of 126 countries observed over
1992-2009, applying the same two exclusion criteria they state (p.
1001): countries with average population below 500,000, and any region
whose entire area lies above 65°N latitude (their own footnote names
Canada, Finland, Iceland, Norway, Russia, Sweden, and Alaska as the
countries this affects), so that every
comparison to the authors' own reported numbers is
like for like rather than an artifact of a different underlying sample.
The authors state a third criterion alongside these two, dropping "the
few regions that are unpopulated" (p. 1001). Table I and Table II apply
a proxy for it: a region is dropped if no population figure could be
matched to it in any observed year, 85 of 38,559 regions (0.06% of
region-years) in this sample. That proxy is not a verified match to the
authors' own concept, since a missing population match reflects either
genuine depopulation or a gap in this project's own population source
reaching that region, and the two cannot be told apart from the data
alone; it is applied anyway, for completeness against the authors'
three-part criterion, because doing so changes essentially nothing:
every coefficient in @tbl-table2 is unchanged to three decimals except
Column (5), which moves by 0.001. Table IV's alternative units of
observation (5km circles, SN1 regions, grid cells) each aggregate
population differently and have no equivalent exclusion built for them,
so this third criterion is not extended there.

## Population and Regional GDP {#sec-pop-gdp}

Two further datasets enter Table II's Columns 7 and 8, not used
elsewhere in the paper. Regional population, needed to construct
per-capita light in Column 7 and as a control in Column 8, comes from
CIESIN's Gridded Population of the World, Version 4 [@ciesin-gpwv4],
zonal-summed to the same ADM2 regions used for the outcome variable.
Column 8's dependent variable, regional GDP, is where this replication
departs most directly from the authors' own construction: the authors
use a regional GDP dataset from @gennaioli2014, which is not publicly
released. This paper substitutes G-Econ 4.0 [@gecon2006], a gridded
regional output dataset aggregated to the same ADM2 regions, as the
closest available public alternative. The two sources are not
interchangeable in their construction, so Column 8's results are
reported as indicative rather than as a like-for-like replication of
the authors' own Column 8, a caveat carried through to @sec-results-table2.

## Descriptive Statistics {#sec-descriptives}

@tbl-descriptives reports summary statistics for the two variables
common to every specification in this paper, nighttime light intensity
and the lagged birth-region dummy, next to the authors' own reported
numbers for the same variables, over the identical 126-country,
1992-2009 sample. Population and regional GDP, the two further
variables introduced in @sec-pop-gdp, are used only in Table II's
Columns 7 and 8 and are not reported here, since the authors' own
descriptive statistics table does not cover them either. The two panels agree closely: mean light intensity
and its dispersion are nearly identical, and the leader dummy's mean,
of order 0.004, matches almost exactly, consistent with only a small
number of a country's many regions being a sitting leader's birth
region in any given year. Leader birth regions are not a random draw
from that pool: the authors report that, on average, they are 40%
larger, five times more populous, and roughly twice as bright at night
as other regions in their own sample (p. 1006), a pre-treatment
imbalance the region and country-year fixed effects in @sec-empirical
are what make the identification strategy hold up despite it. The same
comparison on this paper's own panel agrees on population and light but
not on area: leader birth regions are 5.7 times more populous and 2.2
times as bright, both close to the authors' figures, but only 21% larger
by land area (3,755 km² average against 3,095 km² for other regions),
not 40%, computed over every region in this sample (38,474 of 38,474)
using its GADM 3.6 geometry directly, the same source used throughout
@sec-geometry. The obs. count differs by roughly 5% for
light (655,234 vs. 690,495), which follows directly from using a
different boundary source, as @sec-geometry describes: GADM's ADM2
partition does not divide every country into exactly the same regions
CIESIN's does, so the two panels are built over a similar but not
identical number of region-years.

Leader~ict-1~ is where the two panels initially looked further apart
than that boundary-source gap alone would explain, and checking why
surfaced something worth reporting rather than smoothing over. As a
lagged variable, Leader~ict-1~ should in principle lose the panel's
first year, 1992, since that year's value depends on who governed in
1991, one year before the panel begins. The authors' own reported
figures show no such loss: their Leader~ict-1~ obs. count is exactly
690,495, identical to Light~ict~'s. This is not an error on their
part; Archigos records leader identity for years before 1992 too, so
the 1991 lag can be built from data outside the panel's own stated
window without dropping any 1992 region-years. This paper's own
pipeline did not follow that same convention: 1992's lag was left
missing rather than filled from 1991 data, which by itself accounted
for most of Leader~ict-1~'s shortfall against Light~ict~ (613,178 vs.
655,234, a gap much wider than the boundary-source gap on Light~ict~
alone). Rebuilding the 1992 lag from PLAD and the Wikidata
supplement's pre-1992 leader-tenure records, the same convention the
authors use, raises the observation count to 654,254, with the mean
and standard deviation essentially unchanged. @tbl-descriptives reports
this corrected figure, which matches @tbl-table2's Column (1) exactly,
since both are built from the identical 126-country panel and the same
lag-construction method; the small residual gap to Light~ict~ is the
ordinary GADM-vs-CIESIN boundary-count difference, not a further lag
artifact.

```{r}
#| label: tbl-descriptives
#| tbl-cap: "Descriptive statistics, region-year panel, 126 countries, 1992-2009. Light$_{ict}$ is $\\ln(\\text{Light intensity} + 0.01)$; Leader$_{ict-1}$ is the lagged birth-region dummy. Authors' columns are the corresponding rows of their own reported descriptive statistics table."
#| tbl-pos: "H"

own <- read.csv("../01_datasets/processed/ntl/table1_descriptive_region_hrsample.csv")
leader_fix <- read.csv(
    "../01_datasets/processed/ntl/table1_leader_lag1991fix_hrsample.csv"
)
hr <- read.csv("../01_datasets/processed/ntl/hr2014_table1_reference.csv")

keep <- c("Lightict", "Leaderict-1")
own <- own[match(keep, own$variable), ]
own[own$variable == "Leaderict-1", names(leader_fix)] <- leader_fix[
    1,
    names(leader_fix)
]
hr <- hr[match(keep, hr$variable), ]

fmt <- function(x, digits = 3) {
    formatC(x, format = "f", digits = digits, big.mark = ",")
}
fmt_obs <- function(x) formatC(x, format = "d", big.mark = ",")

label_map <- if (knitr::is_html_output()) {
    c(Lightict = "Light\\(_{ict}\\)", `Leaderict-1` = "Leader\\(_{ict-1}\\)")
} else {
    c(Lightict = "Light$_{ict}$", `Leaderict-1` = "Leader$_{ict-1}$")
}

out <- data.frame(
    Variable = unname(label_map[keep]),
    `Obs.` = fmt_obs(hr$obs),
    Mean = fmt(hr$mean),
    SD = fmt(hr$sd_overall),
    Min = fmt(hr$min),
    Max = fmt(hr$max),
    `Obs. ` = fmt_obs(own$obs),
    `Mean ` = fmt(own$mean),
    `SD ` = fmt(own$sd_overall),
    `Min ` = fmt(own$min),
    `Max ` = fmt(own$max),
    check.names = FALSE
)

knitr::kable(
    out,
    format = if (knitr::is_html_output()) "html" else "latex",
    align = c("l", rep("r", 10)),
    escape = FALSE,
    row.names = FALSE,
    booktabs = TRUE,
    col.names = c(
        "Variable",
        "Obs.",
        "Mean",
        "SD",
        "Min",
        "Max",
        "Obs.",
        "Mean",
        "SD",
        "Min",
        "Max"
    )
) |>
    kableExtra::column_spec(7, border_left = TRUE) |>
    kableExtra::add_header_above(c(
        " " = 1,
        "Authors (126 countries, 1992-2009)" = 5,
        "This Paper (same 126 countries, 1992-2009)" = 5
    )) |>
    kableExtra::kable_styling(font_size = 9)
```

# Empirical Framework {#sec-empirical}

The main specification is a fixed-effects regression at the
region-year level, the same one the authors use:

$$
\text{Light}_{ict} = \alpha_i + \beta_{ct} + \gamma\,\text{Leader}_{ict-1} + \varepsilon_{ict}
$$

$\text{Light}_{ict}$ is log nighttime light intensity for region $i$
in country $c$ in year $t$, and $\text{Leader}_{ict-1}$ is the lagged
birth-region dummy described in @sec-leader-birthplace. $\alpha_i$ is a region
fixed effect: it absorbs everything time-invariant about a region,
geography, permanent infrastructure, its baseline level of
development, so that $\gamma$ is not picking up the fact that some
regions are simply always brighter than others regardless of who
governs. $\beta_{ct}$ is a country-by-year fixed effect: it absorbs
every shock common to all of a country's regions in a given year, a
national election, a currency crisis, a change in the electrification
budget, so that $\gamma$ is not picking up nationwide light growth or
decline that happens to coincide with a leadership change. It also
absorbs a source of variation specific to satellite-recorded light:
DMSP-OLS composites are built from different satellites in different
years, each with its own sensor calibration, and any resulting jump or
drift in recorded brightness is common to every region observed in
that year and is absorbed by $\beta_{ct}$ along with everything else
nationwide. What
survives after both sets of fixed effects are partialed out is
variation within a region, within a country-year: whether a given
region gets brighter relative to the rest of its own country in the
same year, right when it becomes the leader's birth region. This is
also why the specification does not need a set of country or year
fixed effects on their own; the country-by-year interaction subsumes
both.

$\gamma$ is the coefficient of interest. A positive, statistically
significant $\gamma$ is read as evidence of regional favoritism: the
birth region becomes disproportionately brighter than the rest of its
own country, in the same year, precisely while it is a sitting
leader's home region. The authors expect and find $\gamma > 0$; this
paper's replication asks whether that same sign and significance
survive an independently rebuilt version of every input the equation
depends on.

Standard errors are clustered by leader spell, using Archigos
[@goemans2009] to group all region-year observations under the same
leader's tenure together, following the authors' own convention.
Because $\text{Leader}_{ict-1}$ only changes value when a country's
leader changes, region-year observations within a single leader's
spell are not independent draws, and clustering at the country or
region level alone would understate the true correlation in
$\varepsilon_{ict}$ across the years any one leader stays in power.
The cluster definition itself is lagged by one period, the same way
$\text{Leader}_{ict-1}$ is, so that a country-year is grouped with the
spell of the leader who was actually in power the year the regressor
refers to, not the leader in power in the year being clustered.

# Results {#sec-results}

## Main Results and Robustness (Table II) {#sec-results-table2}

@tbl-table2 reports this paper's own estimate of every column of Table
II next to the authors' published numbers, both estimated on the
identical 126-country, 1992-2009 sample described in @sec-geometry, so
region and observation counts are directly comparable column by
column rather than only in sign and significance. Every lagged column
here also carries the same boundary-lag fix documented in
@sec-descriptives for Leader~ict-1~ itself: 1992's lag is filled from
PLAD and the Wikidata supplement's pre-1992 leader-tenure records
rather than left missing, recovering 1992 as an estimation year in
every column that uses the one-year lag. This raises Column (1)'s
observation count to 654,254, close to the authors' own 690,495 and
well above the 613,178 the same specification would show without the
fix, but it also shifts every affected coefficient, and not uniformly
toward the authors' own numbers.

Column (1), the headline specification, the equation of
@sec-empirical estimated exactly as written, gives a birth-region
coefficient of 0.032, significant at the 5% level, against the
authors' own 0.038 at the 1% level: the boundary-lag fix moved this
coefficient down from 0.037 (obtained without the fix) rather than up,
a weaker match to the authors' own number despite being the more
methodologically correct specification.

What that coefficient means in economic terms follows the authors' own
translation. Because the dependent variable is in logs and
Leader~ict-1~ is a dummy, the implied effect on light is
$100(\exp(\gamma) - 1)$ percent: a region is that much brighter while
it is the sitting leader's birth region than the same region would be
if the leader had been born elsewhere. The authors' $\gamma = 0.038$
gives 3.9%; the 0.032 estimated here gives **3.2%**. To get from light
to output the authors use the light-GDP elasticity of roughly 0.3 that
@henderson2012 estimate at the country level and that the authors
confirm at the regional level, which turns their 3.9% into a **1.2%**
increase in regional GDP and this paper's 3.2% into **1.0%**. So the
two panels disagree about the size of the favoritism premium by
roughly a fifth, and agree that it is on the order of one percent of
regional GDP per year of incumbency, concentrated in a single
subnational region. That is small enough to be invisible in national
accounts and large enough to matter locally, and, as the authors note,
it is a lower bound on favoritism itself: leaders who direct resources
somewhere other than their own birth region, or to areas larger or
smaller than one administrative unit, register in this design as
nothing at all.

Columns (2) and (3) exist, in the authors' words, to ensure the main
result "is not an artifact of the lag structure," replacing the
one-year lag with the contemporaneous dummy and a two-year lag
respectively. That robustness holds here too, though unevenly: Column
(3) replicates closely (0.040 against the authors' 0.041, both
significant at the 5% level or better), while Column (2) is the
weaker of the pair at 0.029, significant only at the 10% level against
the authors' own 0.039 at the 1% level.

Columns (4) and (5) are a matched pair, and the authors are explicit
about why. Adding the lagged dependent variable in Column (4) makes
the specification vulnerable to Nickell bias, so, following
@angrist2009, they estimate one specification with fixed effects but
no lagged dependent variable (Column 1) and one with the lagged
dependent variable but no region fixed effects (Column 5), and appeal
to the bracketing property: the true effect should lie between the
two. Their own estimates satisfy it, 0.019 in Column (4) and 0.061 in
Column (5) around a main estimate of 0.038, which is what licenses
their claim that the headline coefficient is "rather conservative and
may even underestimate the true effect." The same bracket holds in
this replication, and independently: 0.026 in Column (4) and 0.050 in
Column (5), with the main estimate of 0.032 sitting inside them. This
is arguably the single strongest form of agreement between the two
panels, because it reproduces not a number but a structural property
of the estimates, and it means the conservative reading the authors
put on their headline coefficient survives here as well.

Column (6), the extensive margin, restricts the outcome to
$\ln(\text{Light}_{ict})$ without the additive constant, dropping
region-years with zero recorded light entirely. The authors report
that the coefficient "becomes somewhat smaller but remains
statistically significant." Here it does not: it falls to 0.008 and
loses significance altogether, against their 0.029 at the 1% level.
This is the clearest genuine non-replication in Table II, and also the
column most affected by the boundary-lag fix. Substantively, it says
the effect found here is carried by regions that were already lit and
became brighter, rather than by dark regions crossing into visibility;
the authors' data supports both channels, this panel's supports only
the first. @sec-discussion returns to it.

Columns (7) and (8) change the dependent variable rather than the
specification, and both replicate in sign and significance. Column (7)
uses light per capita, controlling for regional population, which
distinguishes a region getting brighter because more was built in it
from a region getting brighter because more people moved into it. The
estimate here is 0.025, against the authors' 0.062. The gap is not
only one of magnitude but of direction relative to the baseline: in
the authors' data the per-capita coefficient comes out *larger* than
their main estimate of 0.038, which is what lets them argue the
headline effect is not a population artifact, whereas here it is
*smaller* than the corresponding 0.032. The population denominator
differs between the two panels, GPWv4 here against the authors' own
CIESIN vintage (@sec-pop-gdp), and @sec-discussion returns to the sign
flip on Pop~ict~ itself that accompanies this.

Column (8) replaces light with regional GDP per capita directly, and
is the one column that is not a like-for-like replication by
construction: the authors use @gennaioli2014, which was never
publicly released, so G-Econ 4.0 stands in for it here
(@sec-pop-gdp). The estimate is 0.013 against their 0.021, both
significant. What makes this column valuable despite the substitution
is that it does not rely on the light-GDP elasticity at all. Where
Column (1) reaches output indirectly, 3.2% more light times an assumed
elasticity of 0.3, giving about 1.0%, Column (8) measures it directly
and returns 1.3% on GDP per capita. The two are not the same quantity,
one is regional output and the other output per person, so they need
not coincide exactly; what matters is that two routes resting on
entirely different data and assumptions both land near one percent
rather than near ten or near zero. The same holds in the authors'
data, where the indirect route gives 1.2% and the direct route 2.1%.

Taken as a whole, seven of Table II's eight columns replicate the
authors' finding in both sign and statistical significance on the
identical sample; Column (2) does so only at the 10% level against
their 1%, and Column (6) does not replicate at conventional
significance levels at all. The
qualitative conclusions the authors draw from this table survive: the
effect is not an artifact of lag choice, it is bracketed from both
sides in the Angrist-Pischke sense and therefore plausibly
conservative, and it holds when output is measured directly rather
than inferred from light. What does not survive is the extensive
margin, and the per-capita result holds in a weaker form than in the
authors' own data.

```{r}
#| label: tbl-table2
#| tbl-cap: "Table II replication, all eight columns, in HR 2014's own layout. Both the Orig. and Repl. columns are estimated on the authors' exact 126-country, 1992-2009 sample."
#| tbl-pos: "t"

coefs <- read.csv("../01_datasets/processed/ntl/table2_full_coefs_hrsample.csv")
summ <- read.csv("../01_datasets/processed/ntl/table2_full_summary_hrsample.csv")

row_order <- c("Leader_t-1", "Leader_t", "Leader_t-2", "Light_t-1", "Pop")
row_labels <- c(
    "Leader_t-1" = "Leader$_{ict-1}$",
    "Leader_t" = "Leader$_{ict}$",
    "Leader_t-2" = "Leader$_{ict-2}$",
    "Light_t-1" = "Light$_{ict-1}$",
    "Pop" = "Pop$_{ict}$"
)

cell <- function(source, row, col) {
    r <- coefs[coefs$source == source & coefs$row == row & coefs$col == col, ]
    if (nrow(r) == 0) {
        return("")
    }
    # kableExtra::linebreak() emits \makecell for a two-line cell; \makecell
    # builds its own internal box whose width calculation leaves a hairline
    # sliver at its edges that a colortbl \columncolor background does not
    # reach, showing as a faint vertical seam between the Orig. and Repl.
    # cells of a shaded pair -- but only on \makecell rows, not on the
    # plain-text summary rows below, which is what gave this away.
    # \shortstack (base LaTeX, no box padding of its own) has no such gap.
    sprintf("\\shortstack{%.3f%s\\\\(%.3f)}", r$b, r$sig, r$se)
}

body <- do.call(
    rbind,
    lapply(row_order, function(rn) {
        vals <- character(0)
        for (co in 1:8) {
            vals <- c(vals, cell("hr", rn, co), cell("own", rn, co))
        }
        c(row_labels[[rn]], vals)
    })
)

foot <- rbind(
    c(
        "Number of regions",
        as.vector(rbind(
            as.character(NA),
            formatC(summ$n_regions, big.mark = ",")
        ))
    ),
    c(
        "Observations",
        as.vector(rbind(as.character(NA), formatC(summ$n_obs, big.mark = ",")))
    ),
    c(
        if (knitr::is_html_output()) "Within R\\(^{2}\\)" else "Within $R^2$",
        as.vector(rbind(
            as.character(NA),
            formatC(summ$within_r2, format = "f", digits = 3)
        ))
    ),
    c("Region FE", as.vector(rbind(as.character(NA), summ$region_fe))),
    c("Country-Year FE", as.vector(rbind(as.character(NA), rep("Yes", 8))))
)
foot[1, seq(2, 16, 2)] <- c(
    "38,427",
    "38,427",
    "38,427",
    "38,427",
    "38,427",
    "36,591",
    "37,475",
    "1,207"
)
foot[2, seq(2, 16, 2)] <- c(
    "690,495",
    "690,495",
    "689,870",
    "652,362",
    "652,362",
    "619,594",
    "673,382",
    "14,995"
)
foot[3, seq(2, 16, 2)] <- c(
    "0.319",
    "0.319",
    "0.318",
    "0.412",
    "0.964",
    "0.393",
    "0.197",
    "0.653"
)
foot[4, seq(2, 16, 2)] <- c(
    "Yes",
    "Yes",
    "Yes",
    "Yes",
    "No",
    "Yes",
    "Yes",
    "Yes"
)
foot[5, seq(2, 16, 2)] <- rep("Yes", 8)

out <- rbind(body, foot)
colnames(out) <- c("", rep(c("Orig.", "Repl."), 8))

notes_text <- paste(
    "Fixed-effect regressions, except Column (5), which is standard OLS,",
    "using annual data for subnational regions between 1992 and 2009.",
    "Light$_{ict}$ is the log of average nighttime light intensity plus 0.01.",
    "Light0$_{ict}$ is the log of average nighttime light intensity, without",
    "adding a constant. Lightpc$_{ict}$ is the log of nighttime light",
    "intensity per capita plus 0.01. RegionalGDP$_{ict}$ is the log of",
    "regional GDP per capita, G-Econ 4.0 in the Repl. columns, substituting",
    "for the authors' unreleased Gennaioli et al. (2014) source (Section 3.4).",
    "Leader$_{ict}$ is a dummy variable equal to 1 if region $i$ is the birth",
    "region of the political leader in country $c$ in year $t$, and 0",
    "otherwise; the Repl. columns' Leader$_{ict-1}$ additionally carries the",
    "boundary-lag fix documented in Section 3.5, filling 1992 from pre-1992",
    "leader-tenure records rather than dropping it. Pop$_{ict}$ is the log of",
    "regional population. Standard errors, in parentheses, are clustered by",
    "leader spell, lagged one period.",
    "$^{***}$, $^{**}$, $^{*}$ indicate significance at the 1\\%, 5\\%, and",
    "10\\% levels, respectively."
)

# column_spec(background=...) emits \cellcolor per cell, which never bleeds
# into the surrounding \tabcolsep gap, leaving a visible seam between the
# Orig. and Repl. cells of the same shaded pair (same bug as Table IV, fixed
# there with \columncolor at the column-TYPE level instead). Replicated here:
# align must be a genuine per-column VECTOR, not one pre-concatenated string
# -- passing a single string previously made kable silently repeat it across
# every column and corrupt the tabular preamble (found by inspecting the
# generated .tex directly; this looked identical to "no change" on screen).
shaded2 <- c(3, 4, 7, 8, 11, 12, 15, 16) # data-column index (1-16)
col_type2 <- vapply(
    seq_len(16),
    function(i) {
        if (i %in% shaded2) ">{\\columncolor{gray!10}}c" else "c"
    },
    character(1)
)
align2 <- c("l", col_type2)

if (knitr::is_html_output()) {
    # The LaTeX branch below (\shortstack, \columncolor, a manual
    # \resizebox/tabularx rewrite) has no HTML equivalent, so this branch
    # rebuilds the same table directly as an HTML string instead of trying
    # to route it through kableExtra's LaTeX-oriented helpers.
    row_labels_html <- c(
        "Leader_t-1" = "Leader\\(_{ict-1}\\)",
        "Leader_t" = "Leader\\(_{ict}\\)",
        "Leader_t-2" = "Leader\\(_{ict-2}\\)",
        "Light_t-1" = "Light\\(_{ict-1}\\)",
        "Pop" = "Pop\\(_{ict}\\)"
    )
    cell_html <- function(source, row, col) {
        r <- coefs[coefs$source == source & coefs$row == row & coefs$col == col, ]
        if (nrow(r) == 0) {
            return("")
        }
        sprintf(
            '%.3f%s<br><span class="ptbl-se">(%.3f)</span>',
            r$b, r$sig, r$se
        )
    }
    spec_labels <- c(
        "(1) Light\\(_{ict}\\)", "(2) Light\\(_{ict}\\)",
        "(3) Light\\(_{ict}\\)", "(4) Light\\(_{ict}\\)",
        "(5) Light\\(_{ict}\\)", "(6) Light0\\(_{ict}\\)",
        "(7) Lightpc\\(_{ict}\\)", "(8) RegionalGDP\\(_{ict}\\)"
    )

    thead <- paste0(
        "<tr><th></th>",
        paste0(sprintf('<th colspan="2">%s</th>', spec_labels), collapse = ""),
        "</tr><tr><th></th>",
        paste0(rep("<th>Orig.</th><th>Repl.</th>", 8), collapse = ""),
        "</tr>"
    )

    body_rows_html <- vapply(row_order, function(rn) {
        cells <- vapply(1:8, function(co) {
            shade <- if (co %in% c(2, 4, 6, 8)) ' class="ptbl-shade"' else ""
            sprintf(
                "<td%s>%s</td><td%s>%s</td>",
                shade, cell_html("hr", rn, co), shade, cell_html("own", rn, co)
            )
        }, character(1))
        sprintf(
            "<tr><td>%s</td>%s</tr>",
            row_labels_html[[rn]], paste(cells, collapse = "")
        )
    }, character(1))

    foot_rows_html <- vapply(seq_len(nrow(foot)), function(i) {
        cells <- vapply(2:17, function(j) {
            spec_idx <- ((j - 2) %/% 2) + 1
            shade <- if (spec_idx %in% c(2, 4, 6, 8)) ' class="ptbl-shade"' else ""
            sprintf("<td%s>%s</td>", shade, foot[i, j])
        }, character(1))
        cls <- if (i == 1) ' class="ptbl-foot-first"' else ""
        sprintf("<tr%s><td>%s</td>%s</tr>", cls, foot[i, 1], paste(cells, collapse = ""))
    }, character(1))

    notes_html <- gsub("\\$([^$]*)\\$", "\\1", paste(notes_text, collapse = " "))
    notes_html <- gsub("_\\{([^}]*)\\}", "\\\\(_{\\1}\\\\)", notes_html)
    notes_html <- gsub("\\\\%", "%", notes_html)
    notes_html <- gsub("\\^\\{([^}]*)\\}", "\\\\(^{\\1}\\\\)", notes_html)

    knitr::asis_output(paste0(
        '<div class="ptbl-wrap"><table class="ptbl"><thead>', thead, "</thead><tbody>",
        paste(body_rows_html, collapse = ""),
        paste(foot_rows_html, collapse = ""),
        "</tbody></table></div>",
        '<p class="ptbl-notes"><em>Notes.</em> ', notes_html, "</p>"
    ))
} else {
    tbl <- knitr::kable(
        out,
        format = "latex",
        linesep = "",
        align = align2,
        escape = FALSE,
        row.names = FALSE,
        booktabs = TRUE
    ) |>
        kableExtra::add_header_above(
            c(
                " " = 1,
                "Light$_{ict}$" = 2,
                "Light$_{ict}$" = 2,
                "Light$_{ict}$" = 2,
                "Light$_{ict}$" = 2,
                "Light$_{ict}$" = 2,
                "Light0$_{ict}$" = 2,
                "Lightpc$_{ict}$" = 2,
                "RegionalGDP$_{ict}$" = 2
            ),
            escape = FALSE
        ) |>
        kableExtra::add_header_above(c(
            " " = 1,
            "(1)" = 2,
            "(2)" = 2,
            "(3)" = 2,
            "(4)" = 2,
            "(5)" = 2,
            "(6)" = 2,
            "(7)" = 2,
            "(8)" = 2
        )) |>
        kableExtra::row_spec(5, extra_latex_after = "\\midrule") |>
        kableExtra::kable_styling(font_size = 9)

    tbl_attrs <- attributes(tbl)
    tbl <- sub(
        "\\begin{tabular}",
        paste0(
            "\\resizebox{\\ifdim\\width>\\linewidth\\linewidth\\else\\width\\fi}{!}{",
            "\\begingroup\\setlength{\\tabcolsep}{2.5pt}\\begin{tabular}"
        ),
        tbl,
        fixed = TRUE
    )
    tbl <- sub("\\end{tabular}", "\\end{tabular}\\endgroup}", tbl, fixed = TRUE)
    attributes(tbl) <- tbl_attrs

    # kableExtra::footnote(threeparttable = TRUE) nests threeparttable INSIDE
    # kable_styling's resizebox, which silently clips the note text past the
    # box resizebox measured before scaling. Appending the note as plain LaTeX
    # text after the resizebox's closing brace avoids that: the note renders at
    # its own (unscaled) size, directly under the table, in the same float.
    notes_latex <- paste0(
        "\n\n\\vspace{2mm}\n\n\\begingroup\\footnotesize\\textit{Notes.} ",
        paste(notes_text, collapse = " "),
        "\\endgroup\n"
    )
    tbl_final <- paste0(tbl, notes_latex)
    attributes(tbl_final) <- attributes(tbl)
    tbl_final
}
```


## Geographic Extent (Table IV) {#sec-results-table4}

Table IV asks a different question than Table II: not whether the
birth-region effect exists, but how far it extends. Each of the seven
columns keeps the same specification and re-runs it on a different
definition of "region," shrinking or coarsening the spatial unit
without changing anything else. @fig-erdogan-units shows what those
units actually look like on the ground, drawn on one real birthplace,
Recep Tayyip Erdoğan's, in Kasımpaşa on Istanbul's Golden Horn, rather
than described in the abstract. Panel A is Column (1): a 5 km circle
around the birth coordinate, clipped to the coastline, the tightest
unit in the table, 58 km² here once the Golden Horn is cut out of it.
Panel B is Column (2): the whole SN1 region, here Istanbul province at
4,757 km², about eighty times the circle. Panel C is Column (3): the
same SN1 region with the birth district, Beyoğlu, cut out of the light
average, 10 km² against the province's 4,757, a hole small enough that
the panel carries an inset to make it visible. In estimation the same
cut is applied to every district that was ever a birthplace, not only
the one drawn here. Panel D is Columns
(4)-(7): the four grid cells containing the same point, at 50, 100,
200, and 400 km, drawn together so the jump in unit size across those
four columns is visible at once. These are equal-area rather than
equal-sided cells, so the nominal 50 km cell covers exactly 2,500 km²
but measures 38 by 66 km at this latitude; the panel draws them uncut,
whereas the estimation averages light only over the part of each cell
that falls on land, which this close to the Bosphorus discards most of
it. Because the four units
differ in area by about four orders of magnitude, each panel is zoomed
to its own unit and carries its own scale bar. All four are built from
this project's own geometry pipeline, using the same GADM 3.6
boundaries, hole-punch procedure, and grid construction that produce
the estimates in @tbl-table4, not schematic illustrations.

::: {.content-visible when-format="pdf"}
![The four units of observation behind Table IV, drawn on Recep Tayyip
Erdoğan's birthplace (28.968°E, 41.032°N). Panels are zoomed
independently and each carries its own scale bar; the inset in Panel C
magnifies the removed birth district. Geometry comes from this
project's own pipeline, except Panel A's circle, redrawn as a smooth
5 km buffer on the same coastline because the stored geodesic buffer's
boundary approximation shows at this magnification.](img/erdogan_gis_units_paper.pdf){#fig-erdogan-units width=95% fig-pos="p"}
:::

::: {.content-visible when-format="html"}
![The four units of observation behind Table IV, drawn on Recep Tayyip
Erdoğan's birthplace (28.968°E, 41.032°N). Panels are zoomed
independently and each carries its own scale bar; the inset in Panel C
magnifies the removed birth district. Geometry comes from this
project's own pipeline, except Panel A's circle, redrawn as a smooth
5 km buffer on the same coastline because the stored geodesic buffer's
boundary approximation shows at this magnification.](img/erdogan_gis_units_paper.png){#fig-erdogan-units width=95%}
:::

```{r}
#| label: tbl-table4
#| tbl-cap: "Table IV replication, all seven columns, both panels on the authors' exact 126-country, 1992-2009 sample. Dependent variable: Light$_{ict}$ throughout. Standard errors in parentheses, clustered by leader spell lagged one period. Units of observation: Col. 1, 5 km circles around the leader's birthplace; Col. 2, SN1 (ADM1) region; Col. 3, SN1 with the birth SN2 (ADM2) district excluded; Cols. 4-7, an equal-area world grid at 50/100/200/400 km resolution."
#| tbl-pos: "p"

t4 <- read.csv("../01_datasets/processed/ntl/table4_full_hrsample.csv")

fmt_cell <- function(source, col) {
    r <- t4[t4$source == source & t4$col == col, ]
    # \shortstack instead of kableExtra::linebreak()'s \makecell -- see the
    # matching comment in Table II's cell() function for why.
    sprintf("\\shortstack{%.3f%s\\\\(%.3f)}", r$b, r$sig, r$se)
}
fmt_cell_html <- function(source, col) {
    r <- t4[t4$source == source & t4$col == col, ]
    sprintf('%.3f%s<br><span class="ptbl-se">(%.3f)</span>', r$b, r$sig, r$se)
}
fmt_int <- function(source, col, var) {
    r <- t4[t4$source == source & t4$col == col, ]
    v <- r[[var]]
    if (is.na(v)) {
        return("")
    }
    formatC(v, format = "d", big.mark = ",")
}

leader_row <- c("Leader$_{ict-1}$")
units_row <- c("Units of observation")
regions_row <- c("Number of regions")
obs_row <- c("Observations")
wr2_row <- c(if (knitr::is_html_output()) "Within R\\(^{2}\\)" else "Within $R^2$")

unit_labels <- c(
    "5 km circle",
    "SN1 region",
    "SN1, excl. birth SN2",
    "50 km grid",
    "100 km grid",
    "200 km grid",
    "400 km grid"
)

for (co in 1:7) {
    leader_row <- c(leader_row, fmt_cell("hr", co), fmt_cell("own", co))
    units_row <- c(units_row, "", "")
    regions_row <- c(
        regions_row,
        fmt_int("hr", co, "n_regions"),
        fmt_int("own", co, "n_regions")
    )
    obs_row <- c(
        obs_row,
        fmt_int("hr", co, "n_obs"),
        fmt_int("own", co, "n_obs")
    )
    wr2_row <- c(
        wr2_row,
        sprintf("%.3f", t4[t4$source == "hr" & t4$col == co, "within_r2"]),
        sprintf("%.3f", t4[t4$source == "own" & t4$col == co, "within_r2"])
    )
}
region_fe_row <- c("Region FE", rep("Yes", 14))
cy_fe_row <- c("Country-Year FE", rep("Yes", 14))

# "Units of observation" describes the sample rather than a regressor, so it
# belongs in the lower panel with the other specification rows, not in the
# coefficient block above the midrule.
out4 <- rbind(
    leader_row,
    units_row,
    regions_row,
    obs_row,
    wr2_row,
    region_fe_row,
    cy_fe_row
)
colnames(out4) <- c("", rep(c("Orig.", "Repl."), 7))

# Columns (2), (4), (6) are shaded. kableExtra::column_spec(background=...)
# emits \cellcolor per cell, which paints only the cell's own content box --
# never the \tabcolsep gap on either side of it -- so even with \tabcolsep
# shrunk to 2.5pt a visible white hairline survives between the Orig. and
# Repl. cells of the same shaded pair. \columncolor (also colortbl), applied
# at the column-TYPE level in the tabular preamble instead of per cell,
# extends across the full column including both of its tabcolsep gaps and
# closes the seam completely. kableExtra's own "scale_down" latex_option
# cannot be used with it: kable_styling() re-parses the tabular preamble with
# a sub() that cannot handle column types containing braces, and errors. So
# scale_down is dropped from kable_styling() below, and \resizebox is added
# back by hand afterward, wrapping the exact same tabular kableExtra would
# have.
shaded <- c(3, 4, 7, 8, 11, 12) # data-column index (1-14), excludes the label
col_type <- vapply(
    seq_len(14),
    function(i) {
        if (i %in% shaded) ">{\\columncolor{gray!10}}c" else "c"
    },
    character(1)
)
# knitr::kable's align must be a vector with one token PER COLUMN -- passing
# a single already-concatenated string instead makes kable treat that whole
# string as one column's spec and recycle/repeat it to fill all 15 columns,
# corrupting the tabular preamble (found by inspecting paper.tex: the align
# text appeared duplicated end to end, once per column).
align4 <- c("l", col_type)

# Merge each column's Orig./Repl. unit-of-observation cells into one centered
# \multicolumn spanning both, since the label is the same for both. Shaded
# columns (2), (4), (6) need \cellcolor placed INSIDE the \multicolumn's
# content -- shading applied via column_spec() only covers the ordinary
# (non-multicolumn) cells further down, so this row would otherwise be the
# one unshaded gap in an already-shaded column.
shaded_pair <- c(2, 4, 6) # which of the 7 column-pairs are shaded
units_cell <- function(i) {
    fill <- if (i %in% shaded_pair) "\\cellcolor{gray!10}" else ""
    sprintf("\\multicolumn{2}{c}{%s%s}", fill, unit_labels[i])
}
units_line_new <- paste0(
    "Units of observation & ",
    paste(
        vapply(seq_along(unit_labels), units_cell, character(1)),
        collapse = " & "
    ),
    " \\\\"
)

notes4_text <- paste(
    "Fixed-effect regressions using annual data for subnational regions",
    "between 1992 and 2009. Light$_{ict}$ is the log of average nighttime",
    "light intensity plus 0.01. Leader$_{ict}$ is a dummy variable equal to",
    "1 if region $i$ is the birth region of the political leader in country",
    "$c$ in year $t$, and 0 otherwise. Standard errors, in parentheses, are",
    "clustered by leader spell, lagged one period. Units of observation",
    "differ across columns as labeled in the table.",
    "$^{***}$, $^{**}$, $^{*}$ indicate significance at the 1\\%, 5\\%, and",
    "10\\% levels, respectively."
)

if (knitr::is_html_output()) {
    unit_labels_short <- c(
        "5 km circle", "SN1 region", "SN1, excl. birth SN2",
        "50 km grid", "100 km grid", "200 km grid", "400 km grid"
    )
    thead4 <- paste0(
        "<tr><th></th>",
        paste0(sprintf('<th colspan="2">(%d) Light\\(_{ict}\\)</th>', 1:7), collapse = ""),
        "</tr><tr><th></th>",
        paste0(rep("<th>Orig.</th><th>Repl.</th>", 7), collapse = ""),
        "</tr>"
    )
    leader_cells <- vapply(1:7, function(co) {
        shade <- if (co %in% shaded_pair) ' class="ptbl-shade"' else ""
        sprintf(
            "<td%s>%s</td><td%s>%s</td>", shade, fmt_cell_html("hr", co),
            shade, fmt_cell_html("own", co)
        )
    }, character(1))
    units_cells_html <- vapply(seq_along(unit_labels_short), function(i) {
        shade <- if (i %in% shaded_pair) ' class="ptbl-shade"' else ""
        sprintf('<td colspan="2"%s>%s</td>', shade, unit_labels_short[i])
    }, character(1))
    foot4_rows <- list(regions_row, obs_row, wr2_row, region_fe_row, cy_fe_row)
    foot4_html <- vapply(seq_along(foot4_rows), function(i) {
        r <- foot4_rows[[i]]
        cells <- vapply(2:15, function(j) {
            spec_idx <- ((j - 2) %/% 2) + 1
            shade <- if (spec_idx %in% shaded_pair) ' class="ptbl-shade"' else ""
            sprintf("<td%s>%s</td>", shade, r[j])
        }, character(1))
        cls <- if (i == 1) ' class="ptbl-foot-first"' else ""
        sprintf("<tr%s><td>%s</td>%s</tr>", cls, r[1], paste(cells, collapse = ""))
    }, character(1))
    notes4_html <- gsub("\\$([^$]*)\\$", "\\1", paste(notes4_text, collapse = " "))
    notes4_html <- gsub("_\\{([^}]*)\\}", "\\\\(_{\\1}\\\\)", notes4_html)
    notes4_html <- gsub("\\\\%", "%", notes4_html)
    notes4_html <- gsub("\\^\\{([^}]*)\\}", "\\\\(^{\\1}\\\\)", notes4_html)

    knitr::asis_output(paste0(
        '<div class="ptbl-wrap"><table class="ptbl"><thead>', thead4, "</thead><tbody>",
        "<tr><td>Leader\\(_{ict-1}\\)</td>", paste(leader_cells, collapse = ""), "</tr>",
        '<tr class="ptbl-foot-first"><td>Units of observation</td>',
        paste(units_cells_html, collapse = ""), "</tr>",
        paste(foot4_html[-1], collapse = ""),
        "</tbody></table></div>",
        '<p class="ptbl-notes"><em>Notes.</em> ', notes4_html, "</p>"
    ))
} else {
    tbl4 <- knitr::kable(
        out4,
        format = "latex",
        align = align4,
        escape = FALSE,
        linesep = "",
        row.names = FALSE,
        booktabs = TRUE
    ) |>
        kableExtra::add_header_above(c(
            " " = 1,
            "(1)" = 2,
            "(2)" = 2,
            "(3)" = 2,
            "(4)" = 2,
            "(5)" = 2,
            "(6)" = 2,
            "(7)" = 2
        )) |>
        # Every column of Table IV shares one dependent variable, so it spans the
        # whole width rather than repeating above each pair as in Table 4.
        kableExtra::add_header_above(
            c(" " = 1, "Light$_{ict}$" = 14),
            escape = FALSE
        ) |>
        kableExtra::row_spec(1, extra_latex_after = "\\midrule") |>
        kableExtra::kable_styling(font_size = 9)

    tbl4_attrs <- attributes(tbl4)
    # sub()'s replacement argument treats "\\" as backreference syntax, which
    # silently eats literal backslashes out of a LaTeX replacement string (this
    # broke the row's trailing "\\" line terminator on the first attempt, in turn
    # misplacing the next \midrule). regmatches<- assigns replacement text
    # verbatim, with no backslash reinterpretation, so it is used for the one
    # substitution whose pattern needs to be a regex; the other two substitutions
    # use fixed = TRUE (literal pattern AND literal replacement) instead.
    m <- regexpr("Units of observation & [^\n]*\\\\\\\\", tbl4)
    regmatches(tbl4, m) <- units_line_new
    # scale_down was dropped from kable_styling() (see note above), so its
    # \resizebox wrapping is added back by hand, identical to what it would have
    # generated, together with the same \tabcolsep tightening as before.
    tbl4 <- sub(
        "\\begin{tabular}",
        paste0(
            "\\resizebox{\\ifdim\\width>\\linewidth\\linewidth\\else\\width\\fi}{!}{",
            "\\begingroup\\setlength{\\tabcolsep}{2.5pt}\\begin{tabular}"
        ),
        tbl4,
        fixed = TRUE
    )
    tbl4 <- sub("\\end{tabular}", "\\end{tabular}\\endgroup}", tbl4, fixed = TRUE)
    # row_spec(2, extra_latex_after = "\\midrule") appends "\midrule" right after
    # the units row's own line terminator, but leaves that terminator's trailing
    # "\\" dangling on its own -- LaTeX reads "\midrule\\" as \midrule followed by
    # an empty row, which is the extra blank line above "Number of regions".
    tbl4 <- sub("\\midrule\\\\", "\\midrule", tbl4, fixed = TRUE)
    # Placement is set by the chunk's tbl-pos option rather than here: this
    # table and Figure 2 together fill a page, so both are given float-page
    # placement and Quarto, not kableExtra, writes the table environment.
    attributes(tbl4) <- tbl4_attrs

    notes4_latex <- paste0(
        "\n\n\\vspace{2mm}\n\n\\begingroup\\footnotesize\\textit{Notes.} ",
        paste(notes4_text, collapse = " "),
        "\\endgroup\n"
    )
    tbl4_final <- paste0(tbl4, notes4_latex)
    attributes(tbl4_final) <- attributes(tbl4)
    tbl4_final
}
```

The economic question behind this table is stated plainly by the
authors: are the beneficiaries of favoritism "the political leaders'
family and clan members living in rather narrow geographical areas
around the political leaders' birthplace, or many people in relatively
large geographical areas?" A narrow, clan-sized effect and a broad,
province-sized one look identical in Table II, which fixes the unit at
ADM2 and cannot distinguish them. Varying the unit separates them, and
the answer matters for what regional favoritism is: patronage
delivered to a leader's immediate circle, or public investment whose
incidence, whatever its motive, reaches a substantial population.

@tbl-table4 reports all seven columns next to the authors' own
published numbers, all estimated on the authors' 126-country,
1992-2009 sample. Column (1), the tightest unit, a 5 km circle around
the leader's own birthplace, is where the two panels disagree most
sharply, and the disagreement is not merely about significance. The
authors find 0.049, larger than their own ADM2 baseline of 0.038,
and read this as evidence that "regional favoritism strongly benefits
people living close to the political leaders' birthplaces." Here the
circle gives 0.025, statistically indistinguishable from zero and
*smaller* than the corresponding baseline of 0.032. The sign of the
comparison is reversed: their data says the effect intensifies as the
unit tightens onto the birthplace, this panel's says it does not.
@sec-discussion returns to why, since the circles are also the unit
whose construction differs most between the two panels.

Columns (2) and (3) move in the opposite direction, to units larger
than ADM2, and carry the authors' spillover argument. Column (2)
widens to the SN1 region, on the authors' account about 17 times
larger than an SN2 district, a ratio their own region counts confirm
and this panel's reproduce closely at 16 times; their coefficient
"drops by around one third" relative to the ADM2 baseline, from 0.038
to 0.026, and stays significant. The same widening here costs more, a 45% drop from 0.032
to 0.018, and significance is lost. Column (3) is the sharper test:
it keeps the SN1 region but removes every ever-birth SN2 district
from the light average, so whatever remains is favoritism accruing to
neighbours of the birth district rather than to the birth district
itself. The authors' coefficient falls only slightly, to 0.023, which
leaves 61% of their baseline effect intact *outside* the birth
district, and this is what licenses their conclusion that leaders
favor "not only the SN2 region in which they were born but also other
SN2 regions belonging to the same SN1 region," so that favoritism
"tends to benefit rather large geographical areas and, presumably,
many people." In this panel the same operation leaves 0.010, only 32%
of the baseline, and not significant. The spillover is directionally
present but roughly half as large, and too imprecise to support the
authors' inference on its own.

Columns (4) through (7) replace administrative units with a
same-sized rectangular grid. The authors are explicit that this serves
two purposes: tracing how far the effect reaches, and showing that
"our previous results are not an artifact of the different sizes and
shapes of subnational administrative regions across the world," a
modifiable-areal-unit check. That check passes cleanly in both panels,
and is the strongest agreement in this table: at 50 km, the resolution
closest in scale to an ADM2 district, the grid returns 0.036 here
against an ADM2 baseline of 0.032, and 0.043 against 0.038 for the
authors. Two entirely different partitions of the same territory,
one drawn by governments and one drawn by an arbitrary lattice,
recover the same effect to within a few thousandths.

Where the panels part company is how far out the effect persists. The
authors report it significant at 50, 100, and 200 km and only fading
at 400 km. Here it is significant at 50 km (0.036) and 100 km (0.019)
and gone by 200 km. A more informative way to read the decline than
significance alone is to ask how fast it falls. Each step up the grid
quadruples cell area, so a purely local effect, a fixed absolute
increment of light confined to one spot, would be diluted across four
times the area and its coefficient should fall by a factor of four.
Anything slower means the effect genuinely occupies the larger cell.
By that benchmark the authors' effect keeps extending through 200 km
(their 100 km coefficient of 0.028 far exceeds the 0.011 that pure
dilution predicts, and 200 km's 0.020 exceeds 0.007), and only at the
200-to-400 km step does it decay at exactly the dilution rate, 0.005
predicted against 0.005 observed, marking the outer edge of the
footprint. This panel's effect also extends past 50 km (0.019 against
a predicted 0.009) but then decays *faster* than dilution from 100 km
onward, placing its outer edge somewhere between 100 and 200 km.

In economic terms the two panels agree on the shape and disagree on
the reach. Converting as in @sec-results-table2, the authors' 50 km
estimate is 4.4% more light, or about 1.3% more regional output;
this paper's is 3.6% and 1.1%. At 100 km both fall to roughly 2-3%
light and 0.6-0.9% output. So the per-area intensity of favoritism
declines steadily outward in both, which is what one expects if
resources are concentrated near the leader's home and thin out with
distance rather than being spread evenly across a province. The
substantive difference is the size of the area over which that
premium is detectable at all: on the authors' data, a footprint
extending to a few hundred kilometres and therefore plausibly
covering millions of people; on this data, a tighter footprint of
roughly 100 km. Both readings are inconsistent with favoritism as
pure clan-level transfer, since a 50 km cell already covers 2,500
km², far more than a family or a village. Where the authors' evidence
supports the stronger claim that a substantial share of the benefit
reaches large populations well beyond the birth district, this
replication supports it only in weakened form.


## Extension to the 1992-2023 Window {#sec-extension}

The authors' window closes in 2009 because that is where their data
ends, not because anything about the question does. DMSP-OLS runs
through 2013 and VIIRS begins in 2012, so a harmonized series
[@li2020] that splices the two roughly doubles the usable span to
1992-2023. This section re-estimates Columns (1) through (7) of Table
II on that longer panel. Column (8) is not extended, since it depends
on G-Econ regional GDP, which does not run past the replication
window.

Three things change besides the years: the light series, the
population source, and the clustering. Two of the three carry directly
into how the results should be read, so they are set out first.

### Data behind the extension {#sec-extension-data}

**Nighttime lights.** The outcome is the harmonized DMSP/VIIRS series
of @li2020, which applies the stepwise inter-satellite calibration of
@li2017 to produce one continuous global panel from 1992 onward. Its
two halves have different origins: 1992-2013 is inter-calibrated
DMSP-OLS, and 2014 onward is VIIRS converted onto DMSP's own 0-63
digital-number scale, so that the two are directly comparable in
levels. Both halves share 30 arc-second resolution and WGS84, matching
the raw DMSP composites used in @sec-outcome. This project extracted
region-year zonal means from the rasters itself, over the same GADM 3.6
geometry used for the ADM2 replication geometry in @sec-geometry,
giving 1.51 million region-years across 45,913 regions in 174
countries; 99.1% of those rows are ADM2, with ADM1 used only for
countries GADM 3.6 gives no ADM2 breakdown for. The source authors suggest treating digital
numbers at or below 7 as a noise floor; this paper does not apply that
filter, keeping the raw zonal mean and following the same convention
as the replication panel, where thresholds are an analysis choice
rather than something baked into extraction.

The conversion direction matters for reading Column (6). Because
VIIRS is mapped *onto* DMSP's scale rather than the reverse, the
harmonized series does not inherit VIIRS's full dynamic range, and
one might expect the extensive margin to behave the same in both
halves. It does not: the VIIRS half records zero light in 4.1% of
region-years against 9.4% in the DMSP half. Even after compression
onto a 0-63 scale, in other words, the later sensor still resolves
faint light that the earlier one recorded as darkness, which is what
makes the extensive-margin recovery interpretable as a sensor effect
rather than a change in the phenomenon.

**Population.** Column (7) needs annual regional population over the
full window, which no source provides directly. GHS-POP
[@schiavina2023] publishes benchmarks every five years, and this
project computed zonal population sums for 1990, 1995, 2000, 2005,
2010, 2015 and 2020 over the same ADM2 geometry, then interpolated
linearly between consecutive benchmarks in levels rather than logs,
after aggregation to the region rather than on the raster. The result
covers 45,962 regions in 166 countries.

One limitation is worth stating rather than burying. The last
benchmark used here is 2020, so values for 2021-2023 are not
interpolated between two observed anchors; they are held flat at the
2020 level. Those three years are the weakest part of the population
series, and Column (7) is the only column that depends on it. Because
that is a real weakness, it was tested rather than assumed harmless:
re-estimating Column (7) on 1992-2020, which drops the flat tail
entirely, and again on 1992-2015, where every year lies between two
observed benchmarks, moves the birth-region coefficient by less than
0.002 and changes no conclusion. Three flat years at the end of a
32-year panel are not what identifies this specification.

A second point about units belongs here, since it materially affected
an earlier version of these results. Population enters twice, once as
the denominator of per capita light and once as a control, and HR
define it in thousands. The interpolated GHS-POP file stores its
`lnpop` column on that scale but its raw count column in persons, and
an early version of the extension code took the denominator from the
latter. Dividing light by population in persons makes the ratio of
order $10^{-4}$, small enough that the additive constant of 0.01 in
$\ln(\text{Light}/\text{Pop} + 0.01)$ dominates it: the dependent
variable's standard deviation fell from 1.81 to 0.26 and Column (7)
was driven to 0.001 and insignificance. The results reported here use
population in thousands throughout, consistent with the replication
panel and with the authors' own definition.

**Leaders and clustering.** Birthplaces come from the same PLAD and
Wikidata sources as the replication (@sec-leader-birthplace), expanded
across the longer window. Clustering, however, cannot follow the
replication's convention: Archigos 4.1 stops recording leader spells
in 2015, so leader-spell clusters are undefined for roughly a third of
the extension window. Standard errors are therefore clustered at the
country level throughout the extension. This is the more conservative
choice of the two available, since country clusters are strictly
coarser than leader-spell clusters, and it is applied to all seven
columns rather than only the later years, so that the columns remain
comparable to each other.

### Results over the extended window {#sec-extension-results}

@tbl-extension reports the results. The headline finding is that the
effect does not fade over the longer horizon; it grows. Column (1)
rises from 0.032 on the replication window to 0.048 over 1992-2023,
significant at the 1% level on roughly 1.3 million region-years across
45,463 regions. In the terms of @sec-results-table2 that is 4.9% more
light, or about 1.5% more regional output, against 3.2% and 1.0% on
the shorter window, and it also exceeds the authors' own 1992-2009
estimate of 3.9% and 1.2%. The lag-robustness columns move with it,
0.043 contemporaneous and 0.046 at two years, and the
Angrist-Pischke bracket that held in @sec-results-table2 holds here
too, with Column (4) at 0.025 and Column (5) at 0.074 straddling the
main estimate.

```{r}
#| label: tbl-extension
#| tbl-cap: "Extension: HR 2014 Table II, Columns (1)-(7), re-estimated on the harmonized DMSP/VIIRS panel over 1992-2023. Column (8) is not extended, since G-Econ regional GDP does not cover the later window."

# Laid out like Tables 2 and 3 (HR 2014's own format): specifications run
# across the top as numbered columns, coefficient over standard error in
# each cell, summary rows underneath. Unlike those tables this one has a
# single panel, since the extension has no published counterpart to sit
# beside.
exs <- read.csv("../01_datasets/processed/ntl/extension_table2_summary.csv")
exc <- read.csv("../01_datasets/processed/ntl/extension_table2_coefs.csv")

cell_e <- function(row, col) {
    r <- exc[exc$row == row & exc$col == col, ]
    if (nrow(r) == 0) {
        return("")
    }
    sprintf("\\shortstack{%.3f%s\\\\(%.3f)}", r$b, r$sig, r$se)
}

row_order_e <- c("Leader_t-1", "Leader_t", "Leader_t-2", "Light_t-1", "Pop")
row_lab_e <- c(
    "Leader_t-1" = "Leader$_{ict-1}$",
    "Leader_t" = "Leader$_{ict}$",
    "Leader_t-2" = "Leader$_{ict-2}$",
    "Light_t-1" = "Light$_{ict-1}$",
    "Pop" = "Pop$_{ict}$"
)

# Coefficient cells are two lines tall (\shortstack), so a plain label sits
# on the baseline of the second line and reads as belonging to the row below.
# \shortstack on the label too gives it the same height and centres it.
body_e <- do.call(
    rbind,
    lapply(row_order_e, function(rn) {
        c(
            sprintf("\\shortstack[l]{%s\\\\~}", row_lab_e[[rn]]),
            vapply(1:7, function(co) cell_e(rn, co), character(1))
        )
    })
)

foot_e <- rbind(
    c(
        "Number of regions",
        formatC(exs$n_regions, format = "d", big.mark = ",")
    ),
    c("Observations", formatC(exs$n_obs, format = "d", big.mark = ",")),
    c(if (knitr::is_html_output()) "Within R\\(^{2}\\)" else "Within $R^2$", sprintf("%.3f", exs$within_r2)),
    c("Region FE", c("Yes", "Yes", "Yes", "Yes", "No", "Yes", "Yes")),
    c("Country-Year FE", rep("Yes", 7))
)

oute <- rbind(body_e, foot_e)
colnames(oute) <- c("", sprintf("(%d)", 1:7))

# Centred, stretchable X column: the seven specification columns share
# whatever width is left over after the row-label column, so the table
# always spans exactly \linewidth.
CX <- ">{\\centering\\arraybackslash}X"
shaded_e <- c(2, 4, 6) # shade alternate specification columns
col_type_e <- vapply(
    seq_len(7),
    function(i) {
        if (i %in% shaded_e) paste0(">{\\columncolor{gray!10}}", CX) else CX
    },
    character(1)
)

notes_e <- paste(
    "Fixed-effect regressions, except Column (5), which is standard OLS,",
    "using annual data for subnational regions between 1992 and 2023 on the",
    "harmonized DMSP/VIIRS series of Li et al. (2020). The dependent variable",
    "is given in the column header: Light$_{ict}$ is the log of average",
    "nighttime light intensity plus 0.01, Light0$_{ict}$ omits the additive",
    "constant, and Lightpc$_{ict}$ is per capita. Leader$_{ict}$ is a dummy",
    "equal to 1 if region $i$ is the birth region of the political leader in",
    "country $c$ in year $t$, entered contemporaneously in Column (2), at a",
    "two-year lag in Column (3), and at a one-year lag elsewhere.",
    "Light$_{ict-1}$ is lagged light and Pop$_{ict}$ is the log of regional",
    "population from this project's own GHS-POP series. Standard errors, in",
    "parentheses, are clustered at the country level, since Archigos 4.1 does",
    "not define leader spells past 2015. Within $R^2$ follows the same",
    "region-demeaned convention as Tables 2 and 3; Column (5) reports full",
    "$R^2$, having no region fixed effects to demean by.",
    "$^{***}$, $^{**}$, $^{*}$ indicate significance at the 1\\%, 5\\%,",
    "and 10\\% levels, respectively."
)

if (knitr::is_html_output()) {
    cell_e_html <- function(row, col) {
        r <- exc[exc$row == row & exc$col == col, ]
        if (nrow(r) == 0) {
            return("")
        }
        sprintf('%.3f%s<br><span class="ptbl-se">(%.3f)</span>', r$b, r$sig, r$se)
    }
    dep_labels_e <- c(rep("Light\\(_{ict}\\)", 5), "Light0\\(_{ict}\\)", "Lightpc\\(_{ict}\\)")
    # Two header rows, matching Table II/IV's own thead structure exactly
    # (DV label row styled via thead tr:first-child, spec-number row via
    # thead tr:last-child) -- a single combined row here would get BOTH
    # rules at once (it is simultaneously first- and last-child), which
    # muddles the two styles together rather than applying either cleanly.
    thead_e <- paste0(
        "<tr><th></th>",
        paste0(sprintf("<th>%s</th>", dep_labels_e), collapse = ""),
        "</tr><tr><th></th>",
        paste0(sprintf("<th>(%d)</th>", 1:7), collapse = ""),
        "</tr>"
    )
    body_e_html <- vapply(row_order_e, function(rn) {
        cells <- vapply(1:7, function(co) {
            shade <- if (co %in% shaded_e) ' class="ptbl-shade"' else ""
            sprintf("<td%s>%s</td>", shade, cell_e_html(rn, co))
        }, character(1))
        sprintf("<tr><td>%s</td>%s</tr>", row_lab_e[[rn]], paste(cells, collapse = ""))
    }, character(1))
    body_e_html <- gsub("\\$([^$]*)\\$", "\\1", body_e_html)
    body_e_html <- gsub("_\\{([^}]*)\\}", "\\\\(_{\\1}\\\\)", body_e_html)
    foot_e_html <- vapply(seq_len(nrow(foot_e)), function(i) {
        cells <- vapply(2:8, function(j) {
            shade <- if ((j - 1) %in% shaded_e) ' class="ptbl-shade"' else ""
            sprintf("<td%s>%s</td>", shade, foot_e[i, j])
        }, character(1))
        cls <- if (i == 1) ' class="ptbl-foot-first"' else ""
        sprintf("<tr%s><td>%s</td>%s</tr>", cls, foot_e[i, 1], paste(cells, collapse = ""))
    }, character(1))
    foot_e_html <- gsub("\\$([^$]*)\\$", "\\1", foot_e_html)
    foot_e_html <- gsub("\\^\\{([^}]*)\\}", "\\\\(^{\\1}\\\\)", foot_e_html)

    notes_e_html <- gsub("\\$([^$]*)\\$", "\\1", paste(notes_e, collapse = " "))
    notes_e_html <- gsub("_\\{([^}]*)\\}", "\\\\(_{\\1}\\\\)", notes_e_html)
    notes_e_html <- gsub("\\\\%", "%", notes_e_html)
    notes_e_html <- gsub("\\^\\{([^}]*)\\}", "\\\\(^{\\1}\\\\)", notes_e_html)

    knitr::asis_output(paste0(
        '<div class="ptbl-wrap"><table class="ptbl"><thead>', thead_e, "</thead><tbody>",
        paste(body_e_html, collapse = ""),
        paste(foot_e_html, collapse = ""),
        "</tbody></table></div>",
        '<p class="ptbl-notes"><em>Notes.</em> ', notes_e_html, "</p>"
    ))
} else {
    tble <- knitr::kable(
        oute,
        format = "latex",
        escape = FALSE,
        linesep = "",
        row.names = FALSE,
        booktabs = TRUE,
        align = c("l", col_type_e)
    ) |>
        kableExtra::add_header_above(
            c(
                " " = 1,
                "Light$_{ict}$" = 5,
                "Light0$_{ict}$" = 1,
                "Lightpc$_{ict}$" = 1
            ),
            escape = FALSE
        ) |>
        kableExtra::row_spec(5, extra_latex_after = "\\midrule") |>
        kableExtra::kable_styling(latex_options = c("hold_position"), font_size = 9)

    # Swap tabular -> tabularx{\linewidth}. kable has no native tabularx mode,
    # so the environment is rewritten here; the column spec it emitted already
    # contains the X columns defined above.
    tble_a <- attributes(tble)
    tble <- sub(
        "\\begin{tabular}{",
        "\\begingroup\\setlength{\\tabcolsep}{3pt}\\begin{tabularx}{\\linewidth}{",
        tble,
        fixed = TRUE
    )
    tble <- sub("\\end{tabular}", "\\end{tabularx}\\endgroup", tble, fixed = TRUE)
    tble <- sub("\\midrule\\\\", "\\midrule", tble, fixed = TRUE)
    attributes(tble) <- tble_a

    notes_e_tex <- paste0(
        "\n\n\\vspace{2mm}\n\n\\begingroup\\footnotesize\\textit{Notes.} ",
        paste(notes_e, collapse = " "),
        "\\endgroup\n"
    )
    tble_attrs <- attributes(tble)
    tble_final <- paste0(tble, notes_e_tex)
    attributes(tble_final) <- tble_attrs
    tble_final
}
```

Two columns deserve separate comment: the one that changes most
between the windows, and the one that changes least.

Column (6), the extensive margin, is the specification that failed to
replicate on the authors' own window, where it fell to 0.008 and lost
significance. Over the extended panel it recovers: 0.035, significant
at the 5% level. This is worth stating plainly because it revises what
@sec-results-table2 could conclude on its own. There the failure
looked like a fragility in the finding; here it looks more like a
limitation of the instrument. DMSP-OLS is comparatively insensitive at
low luminance, so genuinely faint regions are recorded as exact zeros
and drop out of a specification that logs light without an additive
constant. The zero rate in the harmonized series bears this out: 9.4%
of region-years in its DMSP half against 4.1% in its VIIRS half
(@sec-extension-data). The extensive margin reappearing once VIIRS
enters the series is therefore consistent with many of the DMSP-era
zeros having been a sensor floor rather than true darkness. The window
and the sensor do change together here, so this panel cannot fully
separate them, but the zero counts point at the sensor.

Column (7), per capita light, gives 0.026 over the extended window
against 0.025 on the replication window, which is about as close an
agreement as any column in this paper produces. That is worth
underlining because the two estimates share almost nothing on the
input side: different light series, different population source
(GPWv4 against GHS-POP), different window, different clustering. The
per-capita result is the one @sec-results-table2 flagged as weaker
than the authors' own, and it is also the one whose population control
carries a sign this paper cannot match to theirs (@sec-discussion).
Both of those remain true; what the extension adds is that the
birth-region coefficient itself is stable across two largely
independent constructions of the same specification.

In economic terms, converting as in @sec-results-table2, the
favoritism premium is roughly half again as large over the longer
window as over the replication window. Column (1)'s 0.048 is 4.9% more
light, or about 1.5% more regional output per year of incumbency,
against 3.2% and 1.0% on 1992-2009, and above the authors' own 3.9%
and 1.2%. The other columns bracket that figure the way one would
expect rather than scattering: the demanding dynamic specification in
Column (4) puts the floor at 2.5% light and 0.75% output, the
no-region-fixed-effects specification in Column (5) puts the ceiling
at 7.7% and 2.3%, and the ratio between ceiling and floor is 3.0 here
against 1.9 on the replication window (Column (4)'s 0.026 and Column
(5)'s 0.050 there), so the bracket has widened somewhat as the panel
has doubled in length, driven by Column (5)'s larger coefficient
rather than any change at the floor. Column (7), which
measures the same thing per person rather than per region, gives 2.7%
against 2.5% on the shorter window. Read together, the estimates say
that a region gains on the order of one to one and a half percent of
output in each year its native son or daughter holds office, and that
this figure is if anything a little larger in the 2010s and 2020s than
it was in the 1990s.

Whether that increase reflects more favoritism or better measurement
is not settled by this panel. The rise is concentrated in exactly the
columns where the sensor change should matter most, and Column (4),
the one column whose identification leans on within-region dynamics
rather than levels, is also the one column that does not rise at all,
holding at 0.025 against 0.026 on the replication window. That pattern
is at least as consistent with VIIRS resolving light that DMSP missed
as with leaders having become more generous to their birthplaces.
What the extension does establish is the negative claim, and it is the
one that matters for the paper's purpose: the effect is not an
artifact of the window the authors happened to have data for.

Taken together, the extension says the birth-region effect is not an
artifact of the 1992-2009 window. All seven extended columns are
significant, the effect is larger rather than smaller over the longer
period, and the one column that failed in the replication recovers
once a more sensitive sensor is in the series.



# Discussion and Limitations {#sec-discussion}

Four results in this paper depart from the authors', and each is
reported where it arises. This section does not restate them. It asks
what each departure should do to a reader's confidence in the
underlying finding, which is a different question and, for a
replication, the more important one.

**A null that belongs to the instrument.** The extensive margin is the
one Table II column that fails outright on the replication window, and
taken alone it would be the paper's most damaging result. The
extension changes what it can mean. Recovering the same specification
on a series with a more sensitive sensor, alongside a halving of the
region-years recorded as perfectly dark, points to the DMSP-era zeros
being a detection floor rather than genuine darkness
(@sec-extension-data). The caution is that window and sensor move
together in the extension, so this is an interpretation the data
permit rather than one it forces. Read conservatively, the column
should be treated as uninformative on 1992-2009 rather than as
evidence against favoritism.

**A discrepancy this paper cannot explain.** The population control
enters with the opposite sign to the authors' in every specification
that includes it, across two population products and both windows.
Stability across independent sources makes a coding error on this side
unlikely, but nothing here identifies the cause, and it would be
dishonest to present a guess as a finding. What limits the damage is
that Pop is a control rather than the estimand, and that the
birth-region coefficients in the columns carrying it agree closely
with each other. The appropriate response is not to discount the
paper's estimates but to treat Columns (7) and (8) as its least
settled, and the population question as open.

**A substitution, not a replication.** Column (8) uses G-Econ in place
of the authors' unreleased regional GDP source, over a sample several
times larger. That the two land at a similar output magnitude is
corroboration from an independent direction; it is not evidence that
the two series measure the same quantity at the region level, and the
column should not be counted as a replicated result.

**A disagreement that is probably about measurement.** The 5 km circle
is the only place where this paper reverses a directional claim rather
than a magnitude. It is also the unit built directly from birthplace
coordinates, which differ in source between the two panels, and the
unit small enough for a few kilometres of coordinate error to change
which pixels are counted. That the coarser units in the same table
agree well is what one would expect if the disagreement is about
birthplace precision rather than about how favoritism is distributed
in space. The claim it undermines is the authors' sharpest local one,
not their central one.

**A difference that cannot be removed.** The authors' regions come
from CIESIN and this paper's from GADM, so the two panels never
partition countries identically. This is the most likely source of the
small, uniform differences running through the replication columns,
and it means no result here is a strict recomputation. Every
comparison in this paper is between two constructions of the same
design, which is the point of the exercise but also its ceiling: a
gap of a few thousandths is not attributable to anything in
particular.

Taken together, one failure has a plausible instrumental explanation,
one is genuine and unexplained but confined to a control, one rests on
a substituted source, and one is confounded with measurement
precision. Against them stands a birth-region coefficient that is
positive and significant across two light series, two population
sources, two boundary vintages, seven spatial units, and a panel twice
the original length. The finding survives; the qualifications are
about how much weight individual columns can bear, not about whether
the effect is there.

# Conclusion {#sec-conclusion}

This paper set out to test whether @hodler2014's finding survives being
rebuilt rather than re-run. Nothing was inherited from their processed
panel: the boundaries come from GADM rather than CIESIN, the
birthplaces from PLAD and a Wikidata supplement rather than their own
geocoding, and the light values from raw satellite composites
extracted here. On that independently assembled data, a region is
about 3% brighter while it is the sitting leader's birth region,
against their 4%, which on the standard light-output elasticity is
roughly one percent of regional output for each year of incumbency.
Seven of Table II's eight columns reproduce the result, and Table IV's
spatial pattern, an effect concentrated near the birthplace and
decaying as the unit of observation widens, reproduces as well.

Extending the panel to 2023 on a harmonized DMSP/VIIRS series
strengthens rather than weakens the case. Every specification is
significant over the longer window and the coefficient rises to 0.048,
about 1.5% of regional output per year in office. It also resolves the
one column that failed on the original window: the extensive margin,
insignificant on DMSP-only data, returns at conventional levels once
VIIRS enters the series, alongside a halving of the share of
region-years recorded as perfectly dark. That is a useful reminder
that a null in this literature can belong to the instrument rather
than to the world.

Two things did not come out clean, and they are worth carrying
forward rather than filing away. The population control enters with
the opposite sign to the authors' in every specification that includes
it, across two population products and both windows, and this paper
cannot explain why. The 5 km circle, the tightest unit in Table IV,
reverses their directional conclusion, though it is also the unit most
exposed to birthplace-coordinate precision and so the least
diagnostic. Neither disturbs the central estimate, but both mark
places where a reader should not treat the replication as settled.

Five further tables from the original, Tables I, III, V, VI, and VII,
were replicated in the course of this project but fall outside the
scope of the argument here; they are reported in the Supplementary
Materials.

The broader point is about what a replication of this kind can
establish that a re-estimation cannot. Running an author's code on an
author's data tests arithmetic. Rebuilding the measurement chain, and
finding the same answer through different boundaries, different
birthplace records, different sensors and a panel twice as long, tests
whether the finding was ever about the particular way the data
happened to be assembled. On the evidence here, it was not.

# Data and Code Availability {.unnumbered}

All data are drawn from open sources: subnational boundaries from
GADM [@gadm36], nighttime lights from DMSP-OLS [@noaa-dmsp] and the
harmonized DMSP/VIIRS series used in the extension [@li2017; @li2020],
leader identities and tenure from Archigos [@goemans2009], birthplaces
from PLAD [@plad2024] supplemented by a Wikidata scrape, and population
from GPWv4 [@ciesin-gpwv4] and this project's own GHS-POP pipeline
[@schiavina2023]. The complete pipeline that builds the panel and
produces every table and figure in this paper is openly available in
the replication repository
(<https://github.com/ofurkancoban/Regional_Favoritism_Replication>).
For space, five further replicated tables discussed in the text,
Table I's full descriptive statistics, Table III's dynamics
specification, Table V's determinants, Table VI's continent split, and
Table VII's aid/oil heterogeneity test, are reported in the
Supplementary Materials rather than here, and leave the conclusions
above unchanged.

# Declaration of AI Use {.unnumbered}

During the preparation of this work, the author used Anthropic Claude
Sonnet 5 for coding assistance in building the
replication pipeline and for English-language improvement of the
manuscript text. After using this tool, the author reviewed and edited
the content as needed and takes full responsibility for the content of
this publication.

# References {.unnumbered}

::: {#refs}
:::

<!--
APPENDIX (does not count toward the 15-page limit): variable
definitions table, additional robustness notes that are still essential
to reading Table II/IV (not the full supplementary set).
-->
