---
title: "Replication & Extension of Regional Favoritism (Hodler & Raschky, 2014)"
doc-type: "Supplementary Materials"
course-info: "Applied Econometrics Using GIS Techniques · SoSe 2026"
lecturer: "Prof. Dr. Erkan Gören"
author:
  - name: Ömer Furkan Çoban
    email: oemer.furkan.coban@uni-oldenburg.de
    affiliations:
      - name: Carl von Ossietzky University of Oldenburg
        department: Applied Economics and Data Science
        city: Oldenburg
        country: Germany
date: "2026-09-15"
date-format: "DD MMMM YYYY"
abstract: |
  This document reports the replication tables that accompany the main
  paper. The main paper covers Table II (main results), Table IV
  (geographic extent), and the 1992-2023 panel extension; the
  remaining five of the authors' seven main-text tables, Table I,
  Table III, Table V, Table VI, and Table VII, are reported here in
  full.
keywords:
  - Regional favoritism
  - Nighttime lights
  - Replication
  - Supplementary materials
journal:
  name: Applied Econometrics Using GIS Techniques, seminar paper
bibliography: references.bib
csl: ../05_presentation/apa.csl
link-citations: true
execute:
  echo: false
  warning: false
  message: false
format:
  elsevier-pdf:
    keep-tex: true
    template-partials:
      - before-body.tex
    include-in-header:
      # See paper.qmd's matching block for why this footnote is kept
      # per-document rather than shared in before-body.tex: this
      # document points readers back at the main paper instead of
      # describing itself as "the supplementary material".
      text: |
        \usepackage{multicol}
        \usepackage{hyperref}
        \apptocmd{\printFirstPageNotes}{%
          \let\thefootnote\relax
          \footnotetext{\textit{Replication package:\space}\href{https://github.com/ofurkancoban/ofurkancoban-Regional_Favoritism_Replication}{github.com/ofurkancoban/ofurkancoban-Regional\_Favoritism\_Replication}, the full pipeline, code, and data behind every table and figure, including the main paper (Table II, Table IV, and the 1992-2023 panel extension).}%
        }{}{}
    journal:
      formatting: preprint
      model: 3p
      cite-style: authoryear
  html:
    title: "Replication & Extension of Regional Favoritism"
    subtitle: "(Hodler & Raschky, 2014)"
    embed-resources: true
    theme: cosmo
    toc: true
    toc-depth: 2
    number-sections: true
    fig-width: 8
    format-links: false
    include-in-header:
      # Identical to paper.qmd's own html include-in-header block, so
      # the two documents render as one visual project rather than
      # two unrelated pages -- see that file for the design rationale
      # behind each rule.
      text: |
        <link rel="stylesheet" href="https://fonts.googleapis.com/css2?family=Fraunces:opsz,wght@9..144,400;9..144,500;9..144,600;9..144,700&family=Source+Serif+4:opsz,wght@8..60,400;8..60,500;8..60,600&family=IBM+Plex+Mono:wght@400;500&display=swap">
        <style>
        :root{
          --paper:#fbf9f4; --paper-panel:#f3efe3; --ink:#24211c;
          --ink-soft:#6b6459; --ink-faint:#a29a89; --navy:#1d2f52;
          --navy-soft:#3a4d73; --gold:#a97e2f; --gold-soft:#e4d3a8;
          --rule:#e3dac2;
        }
        body{
          background:var(--paper); color:var(--ink);
          font-family:"Source Serif 4",Georgia,"Times New Roman",serif;
          font-size:17px; line-height:1.65;
        }
        h1,h2,h3,h4,h5,h6{
          font-family:"Fraunces",Georgia,serif; color:var(--navy);
          font-weight:600; letter-spacing:-0.01em;
        }
        h1.title{ font-weight:700; font-size:34px; }
        .subtitle, p.subtitle{ font-family:"Fraunces",Georgia,serif; font-style:normal; color:var(--navy); font-weight:600; font-size:34px; }
        .doc-type-label{
          font-family:"Fraunces",Georgia,serif; font-style:italic; font-size:1.15rem;
          letter-spacing:0.02em; color:var(--gold); font-weight:500; margin-top:0.5rem;
        }
        a{ color:var(--navy); }
        a:hover{ color:var(--gold); }
        code, pre, kbd, samp{ font-family:"IBM Plex Mono",ui-monospace,monospace; }
        pre{ background:var(--paper-panel); border:1px solid var(--rule); border-radius:4px; }
        blockquote{ border-left:3px solid var(--gold); background:var(--paper-panel); padding:0.6rem 1rem; color:var(--ink-soft); }
        hr{ border-color:var(--rule); }
        .quarto-title-block .quarto-title-meta-contents p{ font-family:"Source Serif 4",Georgia,"Times New Roman",serif; font-size:1rem; color:var(--ink); }
        .abstract{ background:var(--paper-panel); border:1px solid var(--rule); border-radius:6px; padding:1rem 1.25rem; }
        .abstract .block-title, div.abstract > .abstract-title{ font-family:"Fraunces",serif; color:var(--navy); font-weight:600; margin-top:0; }

        @media (min-width: 992px) {
          body .page-columns{
            display:grid; gap:0;
            grid-template-columns:
              [screen-start] 1.5em [screen-start-inset] 3fr
              [page-start page-start-inset] 35px [body-start-outset] 35px
              [body-start] 1.5em
              [body-content-start] minmax(500px, calc(1180px - 3em)) [body-content-end]
              1.5em [body-end] 35px [body-end-outset] minmax(140px, 220px)
              [page-end-inset] 35px [page-end] 3fr
              [screen-end-inset] 1.5em [screen-end];
          }
        }

        #TOC, nav[role="doc-toc"]{
          font-family:"Source Serif 4",Georgia,"Times New Roman",serif; font-size:0.88em;
          background:var(--paper-panel); border:1px solid var(--rule);
          border-radius:6px; padding:0.9rem 1rem;
        }
        #TOC #toc-title, nav[role="doc-toc"] #toc-title{
          font-family:"Fraunces",serif; font-weight:600; color:var(--navy);
          font-size:1.05rem; margin-bottom:0.5rem;
        }
        #TOC ul, nav[role="doc-toc"] ul{ padding-left:0; }
        #TOC a, #TOC a.nav-link, nav[role="doc-toc"] a{
          color:var(--ink-soft) !important; border-left:2px solid transparent;
          padding:0.15rem 0 0.15rem 0.6rem; display:block;
          font-weight:400 !important;
          transition:color .15s, border-color .15s;
        }
        #TOC a:hover, #TOC a.nav-link:hover, nav[role="doc-toc"] a:hover{
          color:var(--navy) !important; border-left-color:var(--gold-soft);
        }
        #TOC a.active, #TOC a.nav-link.active, nav[role="doc-toc"] a.active{
          color:var(--navy) !important; font-weight:600 !important; border-left-color:var(--gold);
        }
        #TOC .quarto-alternate-formats h2, #TOC .quarto-alternate-formats-title{
          font-family:"Fraunces",serif !important; font-weight:600; color:var(--navy);
          font-size:0.95rem; margin:1rem 0 0.4rem; text-transform:none;
        }
        #TOC .quarto-alternate-formats a{
          color:var(--ink-soft) !important; font-weight:400 !important;
          padding:0.15rem 0 0.15rem 0.6rem; border-left:2px solid transparent; display:block;
        }
        #TOC .quarto-alternate-formats a:hover{ color:var(--navy) !important; border-left-color:var(--gold-soft); }
        figcaption, .figure-caption{ font-style:italic; color:var(--ink-soft); font-size:0.9em; }

        table:not(.ptbl){ font-variant-numeric:tabular-nums; }
        table:not(.ptbl) thead th{ font-family:"Fraunces",serif; font-weight:600; color:var(--navy); border-bottom:1.5px solid var(--ink) !important; }
        table:not(.ptbl) td:first-child, table:not(.ptbl) th:first-child{ white-space:nowrap; }
        /* Table 2 (S1) is all compact numeric/SD-triplet cells; nowrap
           throughout keeps the SD column ("2.482, 2.425, 0.538") on one
           line instead of breaking across two or three. */
        #tbl-s1-descriptives table td, #tbl-s1-descriptives table th{ white-space:nowrap; }

        .ptbl-wrap{ width:100%; overflow-x:auto; margin:1.25rem 0; }
        table.ptbl{ width:100%; border-collapse:collapse; font-size:0.78rem; font-variant-numeric:tabular-nums; background:transparent; }
        table.ptbl th, table.ptbl td{ padding:3px 5px; text-align:center; white-space:nowrap; }
        table.ptbl td:first-child, table.ptbl th:first-child{ text-align:left; white-space:nowrap; }
        table.ptbl thead tr:first-child th{ font-family:"Fraunces",serif; font-weight:600; color:var(--navy); border-bottom:none; padding-bottom:2px; }
        table.ptbl thead tr:last-child th{ font-weight:500; color:var(--ink-soft); font-size:0.78em; border-bottom:1.5px solid var(--ink); padding-top:2px; padding-bottom:5px; }
        table.ptbl tbody tr.ptbl-foot-first td{ border-top:1px solid var(--rule); padding-top:6px; }
        table.ptbl tbody tr:last-child td{ border-bottom:1.5px solid var(--ink); }
        table.ptbl .ptbl-shade{ background:var(--paper-panel); }
        table.ptbl .ptbl-se{ color:var(--ink-soft); font-size:0.88em; }
        table.ptbl .ptbl-sub{ color:var(--ink-soft); font-size:0.85em; padding-left:1.25em; }
        .ptbl-notes{ font-size:0.8rem; color:var(--ink-soft); margin-top:0.5rem; line-height:1.5; }
        </style>
    include-after-body:
      text: |
        <script>
        document.addEventListener("DOMContentLoaded", function () {
          // Every link that isn't a same-page anchor opens in a new
          // tab -- see paper.qmd's matching script for the rationale.
          document.querySelectorAll("a[href]").forEach(function (a) {
            if (a.getAttribute("href").charAt(0) !== "#") {
              a.setAttribute("target", "_blank");
              a.setAttribute("rel", "noopener");
            }
          });
          var src = document.getElementById("extra-title-meta-source");
          if (src) {
            var groups = document.querySelectorAll(".quarto-title-meta");
            var target = null;
            groups.forEach(function (g) {
              if (g.textContent.indexOf("Published") !== -1) target = g;
            });
            if (target) {
              while (src.firstChild) target.appendChild(src.firstChild);
            }
            src.remove();
          }
          var linksSrc = document.getElementById("extra-toc-links-source");
          if (linksSrc) {
            var toc = document.getElementById("TOC");
            var formats = toc ? toc.querySelector(".quarto-alternate-formats") : null;
            if (formats && formats.parentNode) {
              formats.parentNode.insertBefore(linksSrc.firstElementChild, formats.nextSibling);
            } else if (toc) {
              toc.appendChild(linksSrc.firstElementChild);
            }
            linksSrc.remove();
          }
          var typeSrc = document.getElementById("extra-doc-type-source");
          if (typeSrc) {
            var titleBlock = document.querySelector(".quarto-title");
            if (titleBlock) {
              titleBlock.appendChild(typeSrc.firstElementChild);
            }
            typeSrc.remove();
          }
        });
        </script>
---

```{r}
#| echo: false
#| results: asis
# Doc-type label ("Supplementary Material"); see paper.qmd's matching
# chunk for the technique.
if (knitr::is_html_output()) {
    knitr::asis_output(paste0(
        '<div id="extra-doc-type-source" style="display:none">',
        '<p class="doc-type-label">Supplementary Material</p>',
        '</div>'
    ))
}
```

```{r}
#| echo: false
#| results: asis
if (knitr::is_html_output()) {
    knitr::asis_output(paste0(
        '<div id="extra-title-meta-source" style="display:none">',
        '<div><div class="quarto-title-meta-heading">Course</div>',
        '<div class="quarto-title-meta-contents"><p>Applied Econometrics Using GIS Techniques</p></div></div>',
        '<div><div class="quarto-title-meta-heading">Semester</div>',
        '<div class="quarto-title-meta-contents"><p>SoSe 2026</p></div></div>',
        '<div><div class="quarto-title-meta-heading">Lecturer</div>',
        '<div class="quarto-title-meta-contents"><p>Prof. Dr. Erkan Gören</p></div></div>',
        '</div>'
    ))
}
```

```{r}
#| echo: false
#| results: asis
if (knitr::is_html_output()) {
    # "Supplementary (HTML)" is dropped below since it's the current
    # page -- see paper.qmd's matching chunk for why. "Paper (HTML)" is
    # added instead so this document links back to the other one. Paths
    # match docs/, the flat GitHub Pages layout `make site` copies this
    # file into -- see paper.qmd's matching chunk for the same note.
    links <- list(
        list(href = "paper.html", icon = "bi-filetype-html", label = "Paper (HTML)"),
        list(href = "Coban_RegionalFavoritismReplication_Paper.pdf", icon = "bi-file-pdf", label = "Paper (PDF)"),
        list(href = "supplementary.html", icon = "bi-filetype-html", label = "Supplementary (HTML)"),
        list(href = "Coban_RegionalFavoritism_Supplementary.pdf", icon = "bi-file-pdf", label = "Supplementary (PDF)"),
        list(href = "presentation.html", icon = "bi-easel2", label = "Presentation (slides)"),
        list(href = "Coban_RegionalFavoritism_Presentation.pdf", icon = "bi-file-pdf", label = "Presentation (PDF)"),
        list(href = "https://github.com/ofurkancoban/ofurkancoban-Regional_Favoritism_Replication", icon = "bi-box-seam", label = "Replication Package")
    )
    links <- Filter(function(l) l$href != "supplementary.html", links)
    items <- vapply(links, function(l) {
        sprintf(
            '<li><a href="%s"><i class="bi %s"></i>%s</a></li>',
            l$href, l$icon, l$label
        )
    }, character(1))
    knitr::asis_output(paste0(
        '<div id="extra-toc-links-source" style="display:none">',
        '<div class="quarto-alternate-formats"><p class="quarto-alternate-formats-title">Other Links</p><ul>',
        paste(items, collapse = ""),
        '</ul></div>',
        '</div>'
    ))
}
```

# Introduction

The main paper covers Table II (the main result), Table IV (the
geographic-extent test), and the 1992-2023 panel extension.
Hodler and Raschky (2014) [@hodler2014] report seven main-text tables
in total; the five this replication also reconstructed but the main
paper does not cover are reported here instead: Table I's full
descriptive statistics (the main paper reproduces only the two
variables common to every specification), Table III's dynamics
specification, Table V's determinants of the effect, Table VI's
continent split, and Table VII's aid/oil heterogeneity test. Every
specification below builds on the same fixed-effects
regression described in the main paper's Section 4 (Empirical
Framework), region and country-by-year fixed effects, standard errors
clustered by leader spell, estimated on the authors' exact 126-country,
1992-2009 sample; that baseline is not restated per section. Data
sources and construction deviations (G-Econ in place of Gennaioli et
al., 2014; a reconstructed WVS-based FamilyTies measure; a more recent
Penn World Table vintage for NationalGDP) follow the same conventions
described in the main paper's Data section.

# Data {#sec-data}

This section lists every data source behind the tables in this
document and in the main paper, in full, since the main paper's Data
section only has room to describe the sources behind Table II and
Table IV. Sources are grouped as they enter the pipeline: the outcome
variable, political-leader identification, geography, population, then
the seven country-level covariates behind Table V, Table VI, and the
extension's determinants and spillover tracks.

@tbl-s0-sources covers every data source behind this document and the
main paper, from the outcome variable through the seven country-level
covariates. DMSP-OLS nighttime lights [@noaa-dmsp] is the dependent
variable throughout, `log(light + 0.01)`, a small constant added
because a large share of region-year observations sit at or near the
lower bound. Archigos [@goemans2009] supplies the base universe of
leader-spells (919 spells, 172 countries) but carries no birthplace of
its own; PLAD [@plad2024] is the primary birthplace source, matching
86.9% of spells, and a Wikidata/Wikipedia scrape [@wikidata-supplement]
fills a further 33 leaders where PLAD has zero coverage, bringing
combined coverage to 90.5%. Geography and population are where this
replication most directly diverges from the authors' own construction,
discussed at length in the main paper's Data section (main paper
Sections 3.3 and 3.4): the authors' CIESIN subnational boundaries
[@ciesin-subadbnd] were never publicly released as underlying data, so
this paper substitutes GADM 3.6 [@gadm36] throughout, and CIESIN's
Gridded Population of the World, versions 3 and 4
[@ciesin-gpwv3; @ciesin-gpwv4], is bridged into one annual series using
their 2000 overlap year as a per-country scaling factor.

The seven country-level covariates used across Table V, Table VI, and
the extension follow. Two are institutional: Polity's
executive-constraints score [@marshall2010] and Barro-Lee's average
schooling [@barrolee2013]. Three are economic and cultural: the Penn
World Table's GDP per capita [@pwt71], Alesina et al.'s linguistic
fractionalization [@alesina2003], and Alesina and Giuliano's family-ties
measure [@alesina2014]. Two are resource-flow controls used in Table
VII's aid/oil heterogeneity test: net official development assistance
[@oecd-ids] and oil rents from the World Bank's adjusted net savings
series [@wb-ans]. The main paper's two documented construction
deviations are both here: NationalGDP comes from a more recent Penn
World Table vintage than the authors' own PWT 7.1, and FamilyTies is
this project's own reconstruction from World Values Survey microdata
(four of the authors' original six waves), since neither of Alesina and
Giuliano's own papers publishes the underlying country lookup table.

None of these sources arrives pre-combined; each table above is the
last link in a chain of merges the main paper's Data section does not
have room to walk through. Birthplace identification runs Archigos and
PLAD through two separate joins before a single leader-spell has a
region: first Archigos's own leader-spell list is matched to PLAD by
leader name and country-year to inherit a birthplace, then PLAD's
coordinate (or the Wikidata gap-fill's, resolved the same way) is
point-in-polygon joined to the GADM 3.6 ADM2 layer, so a spell only
becomes usable once it has cleared both joins; the 90.5% combined
coverage figure in @tbl-s0-sources is the survival rate through that
whole chain, not just the geocoding step. Building $Leader_{ict-1}$
itself is a further merge: a country-year's sitting leader (from the
Archigos/PLAD chain) has to be matched against every region in that
country in that year before the dummy can be defined for regions that
are not the birth region, since a birth-region indicator with no
comparison regions is not a panel variable. The population bridge
merges GPWv3 and GPWv4 on their one shared year, 2000, computing each
country's own GPWv4-to-GPWv3 ratio in that year and using it to rescale
GPWv4's 2005 and 2010 values onto GPWv3's level before the two series
are stacked into one 1990-2010 panel; a small number of countries where
that ratio falls outside [0.85, 1.15], an implausible five-year jump,
have GPWv4 left unscaled rather than forced onto a bridge factor likely
driven by a source break rather than real growth. The seven Table V/VI
covariates and the two Table VII covariates are simpler merges by
comparison, a left join of each country-year covariate value onto
every region-year row for that country in that year, which is also why
Table V/VI/VII's "Number of regions" in @tbl-s3-determinants,
@tbl-s4-continents, and @tbl-s5-aidoil is smaller than the full panel's
38,559: a region drops from a given column's regression only if that
column's own covariate is missing for its country-year, so each
column's own coverage gap, not a shared restriction, sets its region
count.

```{r}
#| label: tbl-s0-sources
#| tbl-cap: "Data sources: outcome variable, political leaders, geography, population, and country-level covariates."
#| tbl-pos: "H"

source("R/comparison_table_helpers.R")

src <- data.frame(
    Source = c(
        "DMSP-OLS Nighttime Lights",
        "Archigos, ext. w/ birthplaces",
        "PLAD Birthplace Coordinates",
        "Wikidata/Wikipedia Scrape",
        "Subnat. Boundaries $\\to$ GADM 3.6",
        "Gridded Population v3 \\& v4",
        "Political Regime Characteristics",
        "Educational Attainment Dataset",
        "Penn World Table, GDP per Capita",
        "Linguistic Fractionalization",
        "Family Ties",
        "Net Official Development Assistance",
        "Adjusted Net Savings, Oil Rents"
    ),
    Coverage = c(
        "Annual 1992-2014, 0-63 DN, all countries; 30 arc-sec ($\\sim$1km), WGS84, unprojected",
        "Leader per country-year to 2004, hand-ext. by HR to 2010; 919 spells, 172 countries",
        "799/919 spells (86.9\\%); zero coverage for 25 countries",
        "108 missing leaders queried, 42 resolved, 33 confirmed in-country",
        "126 countries, 38,427 ADM2 regions; excludes countries under 500k pop. and territory above $65^{\\circ}$N; vector polygons, WGS84, unprojected",
        "Region-year; GPWv3 anchors 1990/95, GPWv4 rev.11 anchors 2000/05/10, bridged and interpolated; GPWv3 2.5 arc-min, GPWv4 5 arc-min, WGS84, unprojected",
        "Country-year, 1800-2010; rescaled Polity2 score, 0 to 1",
        "Country-year, 5-year intervals, 1950-2010",
        "Country-year, US dollars",
        "Country level, time-invariant",
        "Country level, time-invariant",
        "Country-year, current US dollars",
        "Country-year, current US dollars per capita"
    ),
    `Used For` = c(
        "Dependent variable throughout",
        "Defines who led which country and when; builds Experience/TotalTenure; no birthplace itself",
        "Primary birthplace source, point-in-polygon joined to GADM ADM2",
        "Gap-fill only where PLAD has zero coverage; combined coverage 832/919 = 90.5\\%",
        "Regional units of observation; authors' own CIESIN product never publicly released as data",
        "Builds lnpop (log regional population) and per-capita light; 2000 overlap year sets the bridge factor",
        "Executive constraints and political competition; interacted with Leader in Table V",
        "Average years of schooling; second institutional-quality proxy interacted with Leader",
        "Log GDP per capita, baseline economic control (this paper: a more recent PWT vintage than HR's own 7.1)",
        "Probability two random citizens speak different languages; interacted with Leader",
        "Strength of family bonds from World Values Survey; this paper reconstructs it from 4 of the authors' 6 waves",
        "Log ODA per capita; interacted with Leader in Table VII to test whether aid inflows fuel favoritism",
        "Log oil rents per capita; interacted with Leader alongside aid in the same heterogeneity test"
    ),
    check.names = FALSE
)
if (knitr::is_html_output()) {
    src[] <- lapply(src, latex_to_html)
}

knitr::kable(
    src,
    format = if (knitr::is_html_output()) "html" else "latex",
    align = c("l", "l", "l"),
    escape = FALSE,
    row.names = FALSE,
    booktabs = TRUE
) |>
    kableExtra::column_spec(1, width = "3.6cm") |>
    kableExtra::column_spec(2, width = "5.8cm") |>
    kableExtra::column_spec(3, width = "4.6cm") |>
    kableExtra::pack_rows("Outcome Variable", 1, 1) |>
    kableExtra::pack_rows("Political Leaders", 2, 4) |>
    kableExtra::pack_rows("Geography", 5, 5) |>
    kableExtra::pack_rows("Population", 6, 6) |>
    kableExtra::pack_rows("Institutions & Human Capital", 7, 8) |>
    kableExtra::pack_rows("Economic & Cultural Covariates", 9, 11) |>
    kableExtra::pack_rows("External Resource Flows", 12, 13) |>
    kableExtra::kable_styling(font_size = 7, latex_options = "scale_down")
```

One further source, not in the table above because it substitutes
for rather than supplements the authors' own data: Table II Column
(8)'s regional GDP dependent variable. The authors use Gennaioli et al.
(2014) [@gennaioli2014], a subnational regional GDP dataset that is not
publicly released; this paper substitutes G-Econ 4.0 [@gecon2006], a
1-degree grid ($\sim$ 111km, WGS84, unprojected) gridded output dataset
(190 countries, benchmark years 1990/95/2000/05) aggregated to ADM2 by
point-in-polygon join. The two sources are not interchangeable in
construction, so Column (8) is reported as indicative rather than a
like-for-like replication, the same caveat carried through the main
paper's Data and Results sections. @tbl-s1-descriptives below reports
the full observation,
mean, and dispersion comparison between the authors' own panel and this
paper's, for every variable in the table above.

# S1. Table I: Descriptive Statistics (Full Sample) {#sec-s1-table1}

@tbl-s1-descriptives extends the main paper's two-variable descriptive
comparison (Light$_{ict}$, Leader$_{ict-1}$) to the full nine-variable
comparison from the authors' own Table I (p. 1007), including the five
determinants used in Table V and the two spending controls,
Aid$_{ct-1}$ and Oil$_{ct-1}$, in the authors' own layout: the standard
deviation decomposed into overall, between (across regions or
countries), and within (over time) components, following the standard
panel "xtsum" convention, and, for the seven country-level determinants
(Polity$_{ct-1}$ through Oil$_{ct-1}$), a second row in parentheses
giving the same statistics collapsed to one observation per
country-year rather than repeated once per region. The authors do not
report a country-year row for Light$_{ict}$ or Leader$_{ict-1}$ (both
are inherently region-year concepts), so neither does this table.

The two panels agree closely on Light$_{ict}$ and Leader$_{ict-1}$, as
discussed in the main paper's Data section. Of the remaining seven
variables, all seven means and standard deviations sit within a few
percent of the authors' own, including NationalGDP$_{ct-1}$ and
Oil$_{ct-1}$, despite NationalGDP coming from a different Penn World
Table vintage than the authors used and no direct substitute being
available for Oil's original construction; the level-of-development
proxies these variables measure evidently do not depend heavily on
which vintage or source constructs them. Observation counts are also
close for six of the seven, but Aid$_{ct-1}$ is the exception: this
paper's panel matches only 405,473 of the authors' 690,495
region-years, a 41% shortfall, by far the largest gap of any variable
in the table, against 5-11% gaps everywhere else, including
FamilyTies$_c$'s own incomplete reconstruction (covering only four of
the six World Values Survey waves the authors' original source drew
on; see the main paper's Data section for the full account of that
limitation). Aid$_{ct-1}$ does not enter any specification reported in
this document or the main paper, so this gap does not affect any
reported result, but it is the largest single data-coverage difference
between the two panels.

```{r}
#| label: tbl-s1-descriptives
#| tbl-cap: "Descriptive statistics, HR 2014's own layout (p. 1007): region-year panel, 126 countries, 1992-2009. SD is overall, between, within (xtsum decomposition). Rows in parentheses are the same statistics at the country-year level, for Polity$_{ct-1}$ through Oil$_{ct-1}$ only."
#| tbl-pos: "H"

own_ry <- read.csv("../01_datasets/processed/ntl/table1_descriptive_region_hrsample.csv")
own_cy <- read.csv("../01_datasets/processed/ntl/table1_descriptive_countryyear_hrsample.csv")
leader_fix <- read.csv("../01_datasets/processed/ntl/table1_leader_lag1991fix_hrsample.csv")
hr_ry <- read.csv("../01_datasets/processed/ntl/hr2014_table1_reference.csv")

own_ry[own_ry$variable == "Leaderict-1", names(leader_fix)] <- leader_fix[1, names(leader_fix)]

fmt <- function(x, digits = 3) formatC(x, format = "f", digits = digits, big.mark = ",")
fmt_obs <- function(x) formatC(x, format = "d", big.mark = ",")
fmt_sd3 <- function(o, b, w) sprintf("%s, %s, %s", fmt(o), fmt(b), fmt(w))

label_map <- if (knitr::is_html_output()) {
    c(
        Lightict = "Light\\(_{ict}\\)",
        `Leaderict-1` = "Leader\\(_{ict-1}\\)",
        `Polityct-1` = "Polity\\(_{ct-1}\\)",
        `Schoolingct-1` = "Schooling\\(_{ct-1}\\)",
        `NationalGDPct-1` = "NationalGDP\\(_{ct-1}\\)",
        Languagec = "Language\\(_{c}\\)",
        FamilyTiesc = "FamilyTies\\(_{c}\\)",
        `Aidct-1` = "Aid\\(_{ct-1}\\)",
        `Oilct-1` = "Oil\\(_{ct-1}\\)"
    )
} else {
    c(
        Lightict = "Light$_{ict}$",
        `Leaderict-1` = "Leader$_{ict-1}$",
        `Polityct-1` = "Polity$_{ct-1}$",
        `Schoolingct-1` = "Schooling$_{ct-1}$",
        `NationalGDPct-1` = "NationalGDP$_{ct-1}$",
        Languagec = "Language$_c$",
        FamilyTiesc = "FamilyTies$_c$",
        `Aidct-1` = "Aid$_{ct-1}$",
        `Oilct-1` = "Oil$_{ct-1}$"
    )
}
cy_vars <- c("Polityct-1", "Schoolingct-1", "NationalGDPct-1", "Languagec", "FamilyTiesc", "Aidct-1", "Oilct-1")

# HR 2014's own Table I (p. 1007), transcribed directly, region-year
# level and (for the seven determinants) the country-year level too.
hr_ry_extra <- data.frame(
    variable = cy_vars,
    obs = c(684213, 648240, 683669, 679119, 551004, 690495, 645396),
    mean = c(0.789, 8.168, 8.868, 0.318, 0.096, 6.191, 9.357),
    sd_overall = c(0.257, 2.783, 1.147, 0.281, 0.311, 4.743, 4.116),
    sd_between = c(0.239, 2.724, 1.137, 0.281, 0.311, 4.069, 4.457),
    sd_within = c(0.099, 0.570, 0.151, 0.000, 0.000, 2.440, 1.001),
    min = c(0.000, 0.925, 5.080, 0.002, -0.851, -10.632, 0.000),
    max = c(1.000, 13.022, 10.855, 0.923, 0.606, 13.712, 16.396)
)
hr_ry <- data.frame(
    variable = c(hr_ry$variable, hr_ry_extra$variable),
    obs = c(hr_ry$obs, hr_ry_extra$obs),
    mean = c(hr_ry$mean, hr_ry_extra$mean),
    sd_overall = c(hr_ry$sd_overall, hr_ry_extra$sd_overall),
    sd_between = c(c(2.425, 0.045), hr_ry_extra$sd_between),
    sd_within = c(c(0.538, 0.040), hr_ry_extra$sd_within),
    min = c(hr_ry$min, hr_ry_extra$min),
    max = c(hr_ry$max, hr_ry_extra$max)
)
hr_cy <- data.frame(
    variable = cy_vars,
    obs = c(2205, 1922, 2200, 2161, 1112, 2251, 1820),
    mean = c(0.670, 6.968, 8.212, 0.438, 0.041, 7.794, 6.590),
    sd_overall = c(0.312, 2.920, 1.347, 0.298, 0.368, 4.746, 5.262),
    sd_between = c(0.288, 2.891, 1.337, 0.298, 0.371, 4.348, 5.312),
    sd_within = c(0.123, 0.518, 0.180, 0.000, 0.000, 1.931, 1.191)
)

keep <- names(label_map)
own_ry <- own_ry[match(keep, own_ry$variable), ]
hr_ry <- hr_ry[match(keep, hr_ry$variable), ]
own_cy <- own_cy[match(cy_vars, own_cy$variable), ]
hr_cy <- hr_cy[match(cy_vars, hr_cy$variable), ]

fmt_dash <- function(x, digits = 3) ifelse(is.na(x), "--", fmt(x, digits))

ry_rows <- data.frame(
    Variable = unname(label_map[keep]),
    `Obs.` = fmt_obs(hr_ry$obs),
    Mean = fmt(hr_ry$mean),
    SD = fmt_sd3(hr_ry$sd_overall, hr_ry$sd_between, hr_ry$sd_within),
    Min = fmt_dash(hr_ry$min),
    Max = fmt_dash(hr_ry$max),
    `Obs. ` = fmt_obs(own_ry$obs),
    `Mean ` = fmt(own_ry$mean),
    `SD ` = fmt_sd3(own_ry$sd_overall, own_ry$sd_between, own_ry$sd_within),
    `Min ` = fmt_dash(own_ry$min),
    `Max ` = fmt_dash(own_ry$max),
    check.names = FALSE
)
cy_rows <- data.frame(
    Variable = if (knitr::is_html_output()) "&nbsp;&nbsp;&nbsp;&nbsp;(country-year)" else paste0("\\quad (country-year)"),
    `Obs.` = paste0("(", fmt_obs(hr_cy$obs), ")"),
    Mean = paste0("(", fmt(hr_cy$mean), ")"),
    SD = paste0("(", fmt_sd3(hr_cy$sd_overall, hr_cy$sd_between, hr_cy$sd_within), ")"),
    Min = "",
    Max = "",
    `Obs. ` = paste0("(", fmt_obs(own_cy$obs), ")"),
    `Mean ` = paste0("(", fmt(own_cy$mean), ")"),
    `SD ` = paste0("(", fmt_sd3(own_cy$sd_overall, own_cy$sd_between, own_cy$sd_within), ")"),
    `Min ` = "",
    `Max ` = "",
    check.names = FALSE
)

# Interleave: each of the 7 determinant rows gets its country-year row
# directly below it; Light_ict and Leader_ict-1 (rows 1-2) get none.
out <- ry_rows[1:2, ]
for (i in seq_along(cy_vars)) {
    out <- rbind(out, ry_rows[2 + i, ], cy_rows[i, ])
}

knitr::kable(
    out,
    format = if (knitr::is_html_output()) "html" else "latex",
    linesep = "",
    align = c("l", rep("r", 10)),
    escape = FALSE,
    row.names = FALSE,
    booktabs = TRUE,
    col.names = c(
        "Variable",
        "Obs.",
        "Mean",
        "SD (overall, between, within)",
        "Min",
        "Max",
        "Obs.",
        "Mean",
        "SD (overall, between, within)",
        "Min",
        "Max"
    )
) |>
    kableExtra::column_spec(7, border_left = TRUE) |>
    kableExtra::add_header_above(c(
        " " = 1,
        "Authors (126 countries, 1992-2009)" = 5,
        "This Paper (same 126 countries, 1992-2009)" = 5
    )) |>
    kableExtra::kable_styling(font_size = 7, latex_options = "scale_down")
```

# S2. Table III: Dynamics of Regional Favoritism {#sec-s2-table3}

@tbl-s2-dynamics reports the authors' event-study-style specification
(p. 1014-1015), testing whether the birth-region effect is genuinely
tied to a leader's tenure rather than a pre-existing regional trend, in
HR 2014's own row order and variable names. Column (1) adds a one-year
placebo window (Future1$_{ict-1}$, Past1$_{ict-1}$: was this region about
to become, or did it just stop being, the leader's birth region).
Column (2) replaces that with a three-year window (Future3$_{ict-1}$,
Past3$_{ict-1}$, plus the linear trends Pretrend$_{ict-1}$ and
Posttrend$_{ict-1}$ over that window); these two columns test for a
pre-existing or lingering regional trend, not a fixed-effects
specification choice, so neither is a plain baseline the later columns
build on. Columns (3)-(5) keep the three-year placebo window and add
interactions of the birth-region dummy with Experience$_{ct-1}$ (years
the leader has held office so far) and TotalTenure$_{ct-1}$ (the
spell's eventual total length), testing whether the effect grows with
time in office.

An earlier version of this table (and the script generating it) had
guessed this column layout from term counts alone, rather than reading
it directly off HR 2014's own Table III: it put Leader$_{t-1}$ alone in
Column (1) and all four placebo dummies together in Column (2). Checked
directly against the authors' own PDF (p. 1015), that guess was wrong
on both columns, and the sign on Leader $\times$ TotalTenure in Column
(5) was transcribed as positive when the authors report it as negative
(-0.002). Both are corrected here, and the model is re-estimated on the
corrected specification.

The replication's placebo terms stay statistically insignificant in
both Columns (1) and (2), matching the authors' own finding that there
is no detectable pre-trend. The baseline Leader$_{t-1}$ coefficient
stays close to the authors' corresponding value in every column (all
five of the authors' own Leader$_{t-1}$ estimates, 0.038 down to 0.003
across Columns 1-5, are matched within one standard error by this
replication's own; Column (1)'s own estimate, 0.038, now matches the
authors' to three decimals under the corrected specification).

The tenure-accumulation channel is where the two panels part ways. The
authors report a positive, significant Leader $\times$ Experience
effect in both Columns (3) and (5) (0.007 and 0.009, both p<0.01), and
a positive, significant Leader $\times$ TotalTenure effect in Column
(4) (0.005, p<0.01), but their own Column (5) TotalTenure interaction
is small, negative, and not itself significant (-0.002, SE 0.003), so
the authors' own evidence for a TotalTenure channel rests on Column (4)
alone, not on both columns where it appears. This replication's
corresponding interactions are smaller in every column and not
statistically significant anywhere, though they carry the same sign as
the authors' Column (4) throughout. The divergence is specific to this
tenure-accumulation channel, not to the core favoritism effect.

**Reading the columns economically.** Columns (1)-(2) are an
identification check, not a substantive result in their own right: a
region that lights up before its leader takes office, or stays bright
after he leaves, would say the effect is driven by something already
underway in that region rather than by the leader's own presence in
power, undermining the causal story. Both placebo windows coming back
at essentially zero, in both panels, is the paper's evidence that
favoritism is switched on and off with tenure itself, not a proxy for
some slower-moving regional trend. Columns (3)-(5) then ask an economic
question about the mechanism: does favoritism behave like a stock a
leader builds up, or a flow that starts immediately and stays flat?
Experience is the leader's own political capital accumulated so far, a
measure of how consolidated his hold on power is at any given point in
his term; TotalTenure is that same spell's eventual length, known only
in hindsight, so it proxies less for consolidation in real time than
for whatever let this particular leader stay in office as long as he
did (strong patronage networks, weak term limits, favorable political
conditions). HR's own positive, significant coefficients on both
suggest favoritism grows the longer and more securely a leader holds
office, consistent with a patronage relationship that deepens with
tenure rather than one struck once at the start; this replication's
much weaker, insignificant version of the same interactions does not
contradict that story so much as fail to detect it with the same
confidence, given the same-sign point estimates throughout.

```{r}
#| label: tbl-s2-dynamics
#| tbl-cap: "Table III replication, HR 2014's dynamics specification, in the main paper's Orig./Repl. layout and the authors' own row order (p. 1015). Dependent variable: Light$_{ict}$ throughout. Standard errors in parentheses, clustered by leader spell."
#| tbl-pos: "H"

source("R/comparison_table_helpers.R")

m3 <- readRDS("../01_datasets/processed/ntl/table3_dynamics_models.rds")
lb <- "fixest::l(is_birthregion)TRUE"

# HR 2014's own per-column values, transcribed directly from Table III
# (p. 1015); every cell the authors report is populated here, no term
# in their own table is left unreported. Column layout: (1) Leader_t-1 +
# Future1 + Past1; (2) Leader_t-1 + Future3 + Past3; (3) + Leader x
# Experience; (4) + Leader x TotalTenure; (5) both interactions, (2)-(5)
# all keep the three-year placebo window (Future3/Past3/Pretrend/Posttrend).
hr_leader <- list(
    c(0.038, 0.016, "**"), c(0.039, 0.021, "*"), c(0.006, 0.024, ""),
    c(0.003, 0.028, ""), c(0.017, 0.028, "")
)
hr_experience <- list(NULL, NULL, c(0.007, 0.002, "***"), NULL, c(0.009, 0.003, "***"))
hr_totaltenure <- list(NULL, NULL, NULL, c(0.005, 0.002, "***"), c(-0.002, 0.003, ""))
hr_future1 <- list(c(-0.005, 0.029, ""), NULL, NULL, NULL, NULL)
hr_future3 <- list(NULL, c(0.002, 0.025, ""), c(0.006, 0.031, ""), c(0.007, 0.031, ""), c(0.006, 0.031, ""))
hr_pretrend <- list(NULL, NULL, c(-0.005, 0.018, ""), c(-0.005, 0.018, ""), c(-0.005, 0.018, ""))
hr_past1 <- list(c(0.011, 0.024, ""), NULL, NULL, NULL, NULL)
hr_past3 <- list(NULL, c(0.002, 0.020, ""), c(0.007, 0.027, ""), c(0.007, 0.027, ""), c(0.006, 0.027, ""))
hr_posttrend <- list(NULL, NULL, c(-0.001, 0.012, ""), c(-0.001, 0.012, ""), c(-0.001, 0.012, ""))

row_spec <- list(
    list(label = "Leader$_{t-1}$", hr = hr_leader, own = list(m3$m1, m3$m2, m3$m3, m3$m4, m3$m5), term = lb),
    list(label = "Leader $\\times$ Experience$_{ct-1}$", hr = hr_experience, own = list(NULL, NULL, m3$m3, NULL, m3$m5), term = paste0(lb, ":experience_lag")),
    list(label = "Leader $\\times$ TotalTenure$_{ct-1}$", hr = hr_totaltenure, own = list(NULL, NULL, NULL, m3$m4, m3$m5), term = paste0(lb, ":totaltenure_lag")),
    list(label = "Future1$_{ict-1}$", hr = hr_future1, own = list(m3$m1, NULL, NULL, NULL, NULL), term = "future1"),
    list(label = "Future3$_{ict-1}$", hr = hr_future3, own = list(NULL, m3$m2, m3$m3, m3$m4, m3$m5), term = "future3"),
    list(label = "Pretrend$_{ict-1}$", hr = hr_pretrend, own = list(NULL, NULL, m3$m3, m3$m4, m3$m5), term = "pretrend"),
    list(label = "Past1$_{ict-1}$", hr = hr_past1, own = list(m3$m1, NULL, NULL, NULL, NULL), term = "past1"),
    list(label = "Past3$_{ict-1}$", hr = hr_past3, own = list(NULL, m3$m2, m3$m3, m3$m4, m3$m5), term = "past3"),
    list(label = "Posttrend$_{ict-1}$", hr = hr_posttrend, own = list(NULL, NULL, m3$m3, m3$m4, m3$m5), term = "posttrend")
)

n_cols <- 5
body <- do.call(rbind, lapply(row_spec, function(r) {
    vals <- character(0)
    for (co in seq_len(n_cols)) {
        vals <- c(vals, sstack_hr(r$hr[[co]]), sstack_own(r$own[[co]], r$term))
    }
    c(r$label, vals)
}))

# HR 2014's footer (p. 1015) is identical across all five columns, one
# combined event-study sample, not a shrinking one column to column.
s3sum <- read.csv("../01_datasets/processed/ntl/table3_dynamics_summary.csv")
foot <- rbind(
    c("Number of regions", as.vector(rbind("38,427", formatC(s3sum$n_regions, big.mark = ",")))),
    c("Observations", as.vector(rbind("690,495", formatC(s3sum$n_obs, big.mark = ",")))),
    c("$R^2$ / Within $R^2$", as.vector(rbind("0.319", formatC(s3sum$within_r2, format = "f", digits = 3)))),
    c("Region FE", as.vector(rbind("Yes", rep("Yes", n_cols)))),
    c("Country-Year FE", as.vector(rbind("Yes", rep("Yes", n_cols))))
)

out <- rbind(body, foot)
colnames(out) <- c("", rep(c("Orig.", "Repl."), n_cols))

# HR 2014's own Table III note (p. 1015, transcribed verbatim), followed by
# this replication's own additions (column layout recap, R2 comparability
# caveat) appended as a second paragraph rather than interleaved, so the
# authors' own words are not altered by this project's own commentary.
hr_note <- paste(
    "Fixed effect regressions using annual data for subnational regions between 1992 and 2009.",
    "Light$_{ict}$ is the log of average nighttime light intensity plus 0.01.",
    "Leader$_{ict}$ is a dummy variable equal to 1 if region $i$ is the birth region of the political leader in country $c$ in year $t$, and 0 otherwise.",
    "Experience$_{ct}$ is the number of years the political leader has been in power until year $t$.",
    "TotalTenure$_{ct}$ is the total number of years the political leader was in power up to 2010.",
    "Future1$_{ict}$ is a dummy variable equal to 1 if region $i$ is the birth region of the political leader in $t+1$, but not in $t$; and 0 otherwise.",
    "Future3$_{ict}$ is a dummy variable equal to 1 if region $i$ is the birth region of the political leader in $t+1$, $t+2$, or $t+3$, but not in $t$; and 0 otherwise.",
    "Pretrend$_{ict}$ is a time trend for the years in which Future3$_{ict}=1$.",
    "Past1$_{ict}$ is a dummy variable equal to 1 if region $i$ is the birth region of the political leader in $t-1$, but not in $t$; and 0 otherwise.",
    "Past3$_{ict}$ is a dummy variable equal to 1 if region $i$ is the birth region of the political leader in $t-1$, $t-2$, or $t-3$, but not in $t$; and 0 otherwise.",
    "Posttrend$_{ict}$ is a time trend for the years in which Past3$_{ict}=1$.",
    "Standard errors are adjusted for leader clustering.",
    "$^{***}$, $^{**}$, $^{*}$ indicate significance at the 1\\%, 5\\%, and 10\\% levels, respectively. (HR 2014, Table III note, p. 1015.)"
)
own_note <- paste(
    "This replication's own additions: Columns (1)-(5) all use this project's own boundary-lag-corrected Leader$_{ict-1}$ (Section 3.5 of the main paper) and its own construction of Experience/TotalTenure from PLAD/Archigos spells, not the authors' own underlying data.",
    "Column (1) is Leader$_{t-1}$ + Future1 + Past1; (2) is Leader$_{t-1}$ + Future3 + Past3 + Pretrend + Posttrend; (3)-(5) add the Experience and/or TotalTenure interactions on top of Column (2)'s specification.",
    "Orig. $R^2$ above is the authors' own reported $R^2$; Repl. reports this project's within-$R^2$ on the HR/Stata convention (a region-FE-only null model), which is not directly comparable to the authors' figure in level."
)

render_comparison_table(
    out,
    n_cols = n_cols,
    col_headers = c("(1)", "(2)", "(3)", "(4)", "(5)"),
    spanner_label = rep("Light$_{ict}$", n_cols),
    hline_before_foot = nrow(body),
    notes = paste(hr_note, own_note)
)
```

# S3. Table V: Determinants of Regional Favoritism {#sec-s3-table5}

@tbl-s3-determinants reports the authors' cross-sectional determinants
specification (p. 1020-1022), interacting the birth-region dummy with
five country characteristics one at a time (Columns 1-5) and jointly
(Column 6): Polity (a democracy index), Schooling, NationalGDP,
Language (linguistic fractionalization), and FamilyTies. A negative
interaction means the favoritism effect is smaller in countries scoring
higher on that characteristic.

The replication's Column (1) reproduces the authors' central finding
most clearly: the Leader $\times$ Polity interaction is negative and
statistically significant in both panels, of a similar magnitude,
consistent with favoritism being weaker in more democratic countries.
The Leader $\times$ Schooling interaction (Column 2) keeps the authors'
sign, both panels finding weaker favoritism where average schooling is
higher, but loses significance in the replication (the authors' own
estimate is significant at the 1% level, this paper's at neither
level). NationalGDP's interaction (Column 3) also keeps the authors'
sign but loses significance the same way. Language's interaction
(Column 4) is the closest match of the five, both sign and
significance holding up. FamilyTies (Column 5) is the one that
reverses: the authors report a positive, significant interaction,
while this replication's is indistinguishable from zero. These gaps
follow from the same source-construction issues noted in
@sec-s1-table1 (NationalGDP from a different PWT vintage, FamilyTies
from an incomplete WVS reconstruction), though the reversal on
FamilyTies specifically is larger than the Table I comparison alone
would predict.

Column (6)'s combined specification keeps the Polity interaction as
the most stable finding across both panels; the other four covariates
lose significance in the replication once they compete with Polity for
the same underlying cross-country variation, a pattern the authors' own
Column (6) shows to a lesser degree. The one term that changes
qualitatively in Column (6) is the baseline Leader$_{t-1}$ coefficient
itself: the authors' own Column (6) estimate is small, negative, and
not significant (-0.036, SE 0.134), while this replication's is larger,
also negative, and marginally significant (-0.295, SE 0.175), the same
sign, but only the replication's crosses conventional significance.
Because five interaction terms and their lower-order components enter
the same specification, this sign reversal (relative to Columns 1-5,
where Leader$_{t-1}$ stays positive in both panels) is best read as a
symptom of collinearity among the five determinants rather than a
substantive finding on its own.

An earlier version of this table had transcribed the authors' own
Column (6) Leader$_{t-1}$ value as positive (0.036); checked directly
against HR 2014's own Table V (p. 1021), it is negative. This is
corrected below, along with the row order (the authors' own table lists
one row per determinant, Leader $\times$ Polity through Leader $\times$
FamilyTies, each populated in its own column and again in Column (6),
rather than a single generic "Leader $\times$ X" row) and the full
per-column Number of regions, Observations, and $R^2$ footer, which the
authors report varies column to column (684,213 down to 520,081) rather
than staying fixed.

**Reading the columns economically.** Each column asks whether a
different feature of a country's political economy amplifies or damps
the birth-region effect. Column (1)'s Polity interaction is the
paper's institutional-constraints story: in a country with strong
checks and balances, a leader who tried to funnel resources toward his
own region would face opposition parties, an independent judiciary, or
a free press able to expose and contest it, so the favoritism this
paper measures should be smaller precisely where those constraints
bind, which is what the negative interaction says in both panels.
Column (2)'s Schooling interaction reads similarly but through a
different channel, a more educated population being better able to
monitor and punish patronage at the ballot box or through civil
society, so more schooling predicting less favoritism is the same
accountability story from the citizen side rather than the
constitutional side. Column (3)'s NationalGDP interaction is more
ambiguous by construction: a richer country could show less favoritism
because it needs less (public goods are already broadly provided) or
because it has stronger institutions that happen to correlate with
income, or it could show more because a bigger fiscal pie gives a
leader more to redirect. Column (4)'s Language interaction is a
coalition-building story: in a linguistically fractionalized country,
a leader plausibly relies more on visible, targeted transfers to hold
together a coalition across groups, so favoritism being stronger where
fractionalization is higher is consistent with regional patronage
substituting for the national cohesion a shared language would
otherwise provide. Column (5)'s FamilyTies interaction is a
particularism story in the same spirit: where kinship and family
obligation carry more weight than universalistic norms, a leader's own
extended network is a more natural conduit for resources, so stronger
family ties predicting more favoritism fits a clientelist mechanism
operating through personal rather than institutional channels. Column
(6) asks which of these five channels survives once they all compete
for the same explanatory power, and in both panels it is the
institutional one, Polity, that does, consistent with formal political
constraints being a more fundamental brake on favoritism than any of
the four cultural or economic proxies.

```{r}
#| label: tbl-s3-determinants
#| tbl-cap: "Table V replication, HR 2014's determinants specification, in the main paper's Orig./Repl. layout and the authors' own row order (p. 1021). Standard errors in parentheses, clustered by leader spell."
#| tbl-pos: "H"

source("R/comparison_table_helpers.R")

m5 <- readRDS("../01_datasets/processed/ntl/table5_determinants_models.rds")
lb <- "fixest::l(is_birthregion)TRUE"
own_models <- list(m5$m1, m5$m2, m5$m3, m5$m4, m5$m5, m5$m6)

int_terms <- c(
    "fixest::l(is_birthregion)TRUE:fixest::l(polity)",
    "fixest::l(is_birthregion)TRUE:fixest::l(schooling)",
    "fixest::l(is_birthregion)TRUE:fixest::l(national_gdp)",
    "fixest::l(is_birthregion)TRUE:language",
    "fixest::l(is_birthregion)TRUE:family_ties"
)
det_labels <- c(
    "Leader $\\times$ Polity$_{ct-1}$", "Leader $\\times$ Schooling$_{ct-1}$",
    "Leader $\\times$ NationalGDP$_{ct-1}$", "Leader $\\times$ Language$_c$",
    "Leader $\\times$ FamilyTies$_c$"
)

# HR 2014's own Table V (p. 1021), transcribed directly.
hr_leader <- list(
    c(0.262, 0.056, "***"), c(0.119, 0.040, "***"), c(0.196, 0.082, "**"),
    c(-0.008, 0.017, ""), c(0.008, 0.012, ""), c(-0.036, 0.134, "")
)
hr_inter <- list(
    c(-0.298, 0.063, "***"), c(-0.012, 0.004, "***"), c(-0.019, 0.009, "**"),
    c(0.120, 0.040, "***"), c(0.063, 0.032, "**")
)
hr_col6 <- list(
    c(-0.240, 0.065, "***"), c(-0.024, 0.007, "***"), c(0.050, 0.018, "***"),
    c(0.016, 0.052, ""), c(0.035, 0.034, "")
)
hr_n_regions <- c(38427, 36033, 38179, 37795, 30631, 29123)
hr_n_obs <- c(684213, 648240, 683669, 679119, 551004, 520081)
hr_r2 <- c(0.320, 0.330, 0.320, 0.318, 0.308, 0.313)

n_cols <- 6
row_leader <- c("Leader$_{t-1}$", as.vector(sapply(1:n_cols, function(i) {
    c(sstack_hr(hr_leader[[i]]), sstack_own(own_models[[i]], lb))
})))
det_rows <- do.call(rbind, lapply(seq_along(det_labels), function(i) {
    vals <- character(0)
    for (co in 1:n_cols) {
        if (co == i) {
            vals <- c(vals, sstack_hr(hr_inter[[i]]), sstack_own(own_models[[i]], int_terms[i]))
        } else if (co == n_cols) {
            vals <- c(vals, sstack_hr(hr_col6[[i]]), sstack_own(m5$m6, int_terms[i]))
        } else {
            vals <- c(vals, "", "")
        }
    }
    c(det_labels[i], vals)
}))

body <- rbind(row_leader, det_rows)
foot <- rbind(
    c("Number of regions", as.vector(rbind(formatC(hr_n_regions, format = "d", big.mark = ","), formatC(sapply(own_models, function(m) length(fixest::fixef(m)$gid_2)), format = "d", big.mark = ",")))),
    c("Observations", as.vector(rbind(formatC(hr_n_obs, format = "d", big.mark = ","), formatC(sapply(own_models, stats::nobs), format = "d", big.mark = ",")))),
    c("$R^2$", as.vector(rbind(formatC(hr_r2, format = "f", digits = 3), formatC(sapply(own_models, function(m) fixest::r2(m, "r2")), format = "f", digits = 3)))),
    c("Region FE", as.vector(rbind("Yes", rep("Yes", n_cols)))),
    c("Country-Year FE", as.vector(rbind("Yes", rep("Yes", n_cols))))
)
out <- rbind(body, foot)
colnames(out) <- c("", rep(c("Orig.", "Repl."), n_cols))

render_comparison_table(
    out,
    n_cols = n_cols,
    col_headers = c("(1)", "(2)", "(3)", "(4)", "(5)", "(6)"),
    spanner_label = rep("Light$_{ict}$", n_cols),
    hline_before_foot = nrow(body),
    font_size = 6.5,
    notes = paste(
        "Fixed effect regressions using annual data for subnational regions between 1992 and 2009.",
        "Leader$_{ict-1}$ is a dummy variable equal to 1 if region $i$ is the birth region of the political leader in country $c$ in year $t-1$, and 0 otherwise.",
        "Polity$_{ct-1}$ is the Polity2 score, rescaled 0 to 1.",
        "Schooling$_{ct-1}$ is average years of schooling.",
        "NationalGDP$_{ct-1}$ is the log of GDP per capita.",
        "Language$_c$ is an index of linguistic fractionalization.",
        "FamilyTies$_c$ is a measure of the strength of family ties.",
        "Standard errors are adjusted for leader clustering.",
        "$^{***}$, $^{**}$, $^{*}$ indicate significance at the 1\\%, 5\\%, and 10\\% levels, respectively. (HR 2014, Table V note, p. 1021, adapted.)",
        "This replication's own additions: Column (6) interacts the birth-region dummy with all five determinants jointly, so each determinant's row is populated in its own single column and again in Column (6), not a generic \"Leader x X\" row.",
        "NationalGDP and FamilyTies are built from different underlying sources than the authors' own (Section 2).",
        "Orig. $R^2$ is the authors' own reported $R^2$; Repl. reports fixest's overall (not within-transformed) $R^2$, which nets out the region and country-year fixed effects and is mechanically much closer to 1, so the two are not directly comparable in level."
    )
)
```

# S4. Table VI: Favoritism by Continent {#sec-s4-table6}

@tbl-s4-continents decomposes the pooled Leader$_{t-1}$ effect into five
continent-specific terms (p. 1023): Africa, Americas, Asia, Europe, and
Oceania, with no omitted reference category since region and
country-year fixed effects already absorb any continent-level main
effect. Column (1) is the plain decomposition; Column (2) adds the
Polity interaction; Column (3) adds all five Table V determinants.

Column (1) does not reproduce the authors' geographic pattern as
closely as Columns (2)-(3) reproduce their covariate pattern. Asia,
the authors' largest and most significant continent effect (0.121,
p<0.01), loses its significance entirely in this replication (0.036,
not significant), the largest single change in the table.
Africa stays significant in both panels but at a lower confidence
level here (authors' 0.071, p<0.01, against this paper's 0.089,
p<0.05). Europe's sign matches, small and negative in both the
authors' data (-0.019, p<0.1) and here (-0.017, p<0.1), both only
weakly significant; an earlier version of this table had transcribed
the authors' Column (1) Europe and Oceania values as positive, which,
checked against HR 2014's own Table VI (p. 1023), is wrong for both;
Oceania is -0.112 (not significant) in the authors' own data as well,
also matching this replication's sign. Americas and Oceania are not
significant in either panel. Once covariates enter in Columns (2)-(3),
a second, systematic divergence appears: every one of the authors'
five continent coefficients in Column (3) is positive, while every one
of this paper's is negative, the same full sign reversal Column (6) of
Table V shows for the pooled Leader$_{t-1}$ term once all five
determinants enter together (@sec-s3-table5). Column (2), with only
the Polity interaction added, does not show this reversal, so it is
specific to the fully saturated Column (3) specification, consistent
with collinearity among the five determinants rather than five
independent continent-level findings. The Polity interaction itself
stays the most stable term across both panels throughout Columns
(2)-(3), negative and significant in every case though smaller in
magnitude here. Among Column (3)'s other four determinants, the
authors' own NationalGDP interaction is positive (0.047**) rather than
negative; an earlier version of this table's footnote had it as
negative, corrected below.

**Reading the columns economically.** Column (1)'s five continent
coefficients are a first, unconditional look at where in the world
favoritism runs strongest, before any attempt to explain why. Asia and
Africa carrying the largest, most significant effects in the authors'
own data (and Africa still significant, if smaller, in this
replication) is consistent with the countries in HR's sample that fall
in those continents skewing toward weaker political institutions and
more discretionary, personalist rule, exactly the conditions Column
(1) of Table V already flags as predicting more favoritism; Europe's
small, weakly significant coefficient (whichever sign either panel
finds) fits the same story from the other side, since HR's
European sample leans toward the stronger-institution countries Table
V's Polity interaction associates with less favoritism. Column (2)
tests whether that geographic pattern survives once Polity is held
constant within each continent, and it does not: every continent's
coefficient jumps to a similar, large, significant magnitude once
Polity enters, which says the geographic pattern in Column (1) is not
five independent regional cultures of favoritism so much as one
institutional-quality gradient that happens to correlate with
continent, the raw continent effects in Column (1) proxying for
Polity rather than adding anything Polity does not already capture.
Column (3) pushes this further by adding all five Table V determinants
at once, and the continent coefficients lose their earlier sign and
significance entirely, the same collinearity pattern Table V's own
Column (6) shows for the pooled Leader$_{t-1}$ term: once schooling,
income, language, and family ties compete with Polity for the same
underlying cross-country variation, no single term, continent included,
retains a clean, independent read on what actually drives favoritism.

```{r}
#| label: tbl-s4-continents
#| tbl-cap: "Table VI replication, HR 2014's continent-split specification, in the main paper's Orig./Repl. layout and the authors' own row order (p. 1023). Standard errors in parentheses, clustered by leader spell."
#| tbl-pos: "H"

source("R/comparison_table_helpers.R")

m6 <- readRDS("../01_datasets/processed/ntl/table6_continents_models.rds")
lb2 <- "fixest::l(is_birthregion)"
own_models <- list(m6$m1, m6$m2, m6$m3)

continents <- c("africa", "americas", "asia", "europe", "oceania")
cont_labels <- c(
    "Leader $\\times$ Africa$_c$", "Leader $\\times$ Americas$_c$", "Leader $\\times$ Asia$_c$",
    "Leader $\\times$ Europe$_c$", "Leader $\\times$ Oceania$_c$"
)

# HR 2014's own Table VI (p. 1023), transcribed directly.
hr_col1 <- list(
    c(0.071, 0.026, "***"), c(0.000, 0.025, ""), c(0.121, 0.042, "***"),
    c(-0.019, 0.010, "*"), c(-0.112, 0.077, "")
)
hr_col2 <- list(
    c(0.235, 0.047, "***"), c(0.243, 0.067, "***"), c(0.296, 0.073, "***"),
    c(0.239, 0.067, "***"), c(0.106, 0.101, "")
)
hr_col3 <- list(
    c(0.041, 0.167, ""), c(0.056, 0.179, ""), c(0.005, 0.147, ""),
    c(0.035, 0.163, ""), c(0.167, 0.168, "")
)
hr_polity <- list(NULL, c(-0.278, 0.070, "***"), c(-0.252, 0.068, "***"))
hr_schooling <- list(NULL, NULL, c(-0.027, 0.007, "***"))
hr_national_gdp <- list(NULL, NULL, c(0.047, 0.020, "**"))
hr_language <- list(NULL, NULL, c(0.024, 0.046, ""))
hr_family_ties <- list(NULL, NULL, c(0.011, 0.037, ""))

hr_n_regions <- c(38427, 38427, 29123)
hr_n_obs <- c(690495, 684213, 520081)
hr_r2 <- c(0.319, 0.320, 0.313)

n_cols <- 3
cont_rows <- do.call(rbind, lapply(seq_along(continents), function(i) {
    term <- sprintf("%s:%s", lb2, continents[i])
    vals <- as.vector(sapply(1:n_cols, function(j) {
        hr_j <- switch(j, hr_col1[[i]], hr_col2[[i]], hr_col3[[i]])
        c(sstack_hr(hr_j), sstack_own(own_models[[j]], term))
    }))
    c(cont_labels[i], vals)
}))

covariate_row <- function(label, hr_list, term) {
    vals <- as.vector(sapply(1:n_cols, function(j) {
        c(sstack_hr(hr_list[[j]]), sstack_own(own_models[[j]], term))
    }))
    c(label, vals)
}
row_polity <- covariate_row("Leader $\\times$ Polity$_{ct-1}$", hr_polity, sprintf("%s:%s", lb2, "fixest::l(polity)"))
row_schooling <- covariate_row("Leader $\\times$ Schooling$_{ct-1}$", hr_schooling, sprintf("%s:%s", lb2, "fixest::l(schooling)"))
row_national_gdp <- covariate_row("Leader $\\times$ NationalGDP$_{ct-1}$", hr_national_gdp, sprintf("%s:%s", lb2, "fixest::l(national_gdp)"))
row_language <- covariate_row("Leader $\\times$ Language$_c$", hr_language, sprintf("%s:%s", lb2, "language"))
row_family_ties <- covariate_row("Leader $\\times$ FamilyTies$_c$", hr_family_ties, sprintf("%s:%s", lb2, "family_ties"))

body <- rbind(cont_rows, row_polity, row_schooling, row_national_gdp, row_language, row_family_ties)
foot <- rbind(
    c("Number of regions", as.vector(rbind(formatC(hr_n_regions, format = "d", big.mark = ","), formatC(sapply(own_models, function(m) length(fixest::fixef(m)[[1]])), format = "d", big.mark = ",")))),
    c("Observations", as.vector(rbind(formatC(hr_n_obs, format = "d", big.mark = ","), formatC(sapply(own_models, stats::nobs), format = "d", big.mark = ",")))),
    c("$R^2$", as.vector(rbind(formatC(hr_r2, format = "f", digits = 3), formatC(sapply(own_models, function(m) fixest::r2(m, "r2")), format = "f", digits = 3)))),
    c("Region FE", as.vector(rbind("Yes", rep("Yes", n_cols)))),
    c("Country-Year FE", as.vector(rbind("Yes", rep("Yes", n_cols))))
)
out <- rbind(body, foot)
colnames(out) <- c("", rep(c("Orig.", "Repl."), n_cols))

render_comparison_table(
    out,
    n_cols = n_cols,
    col_headers = c("(1)", "(2)", "(3)"),
    spanner_label = rep("Light$_{ict}$", n_cols),
    hline_before_foot = nrow(body),
    font_size = 7,
    notes = paste(
        "Fixed effect regressions using annual data for subnational regions between 1992 and 2009.",
        "Leader$_{ict-1}$ is a dummy variable equal to 1 if region $i$ is the birth region of the political leader in country $c$ in year $t-1$, and 0 otherwise.",
        "Africa$_c$, Americas$_c$, Asia$_c$, Europe$_c$, and Oceania$_c$ are dummy variables for the respective continents.",
        "Polity$_{ct-1}$ is the Polity2 score, rescaled so that it ranges from 0 to 1, with higher values implying stronger political institutions.",
        "Schooling$_{ct-1}$ is the average years of schooling attained.",
        "NationalGDP$_{ct-1}$ is the log of GDP per capita.",
        "Language$_c$ is the index of linguistic fractionalization.",
        "FamilyTies$_c$ is a measure of the strength of family ties.",
        "Standard errors are adjusted for leader clustering.",
        "$^{***}$, $^{**}$, $^{*}$ indicate significance at the 1\\%, 5\\%, and 10\\% levels, respectively. (HR 2014, Table VI note, p. 1023, adapted.)",
        "This replication's own additions: no continent is an omitted reference category, since region and country-year fixed effects already absorb any continent-level main effect; each continent's coefficient is a level effect in its own right, not a contrast against a baseline continent.",
        "Orig. $R^2$ is the authors' own reported $R^2$; Repl. reports fixest's overall (not within-transformed) $R^2$, which nets out the region and country-year fixed effects and is mechanically much closer to 1, so the two are not directly comparable in level."
    )
)
```

# S5. Table VII: Aid, Oil, and Regional Favoritism {#sec-s5-table7}

@tbl-s5-aidoil reports the authors' aid/oil heterogeneity test (p.
1024), asking whether favoritism responds more to a leader's incentives
when a country receives more foreign aid or earns more from oil, and
whether that response depends on the strength of political
institutions. Columns (1)-(2) interact the birth-region dummy with
Aid$_{ct-1}$ and Oil$_{ct-1}$ separately; Columns (3)-(4) add a triple
interaction with Polity$_{ct-1}$, testing whether the aid/oil channel
itself is weaker where institutions are stronger. This table was
already fully built by this project's own pipeline (script and fitted
models) but had not yet been added to this document; it is included
here for completeness against the authors' seven-table set.

This table diverges from the authors' own more than any other in this
document. The authors' central finding, a positive and significant
Leader $\times$ Aid interaction in Column (1) (0.008, p<0.01), does not
reproduce: this replication's Column (1) estimate is smaller and not
itself significant (0.003, SE 0.004). Column (3), which keeps the same
interaction alongside the Polity triple interaction, shows the same
pattern: the authors' Aid interaction there is significant (0.019,
p<0.05), this replication's is not (0.008, SE 0.016). Column (2)'s Oil
interaction diverges in the other direction: the authors' own estimate
is small and not significant (0.000, SE 0.002), while this
replication's is negative and significant (-0.008, p<0.01), the only
term in this table where the replication is significant and the
authors' own is not. The baseline Leader$_{t-1}$ coefficient is not
significant in either panel in Columns (1) and (3), but diverges more
in Columns (2) and (4), where this replication's estimate turns
significant (0.090, p<0.01, and 0.245, p<0.05) against the authors'
own small, insignificant values. The two triple interactions, Aid
$\times$ Polity and Oil $\times$ Polity, keep the authors' negative
sign in three of the four relevant column entries but are not
significant in this replication's version of either, where the
authors report one of the two (Aid $\times$ Polity, Column 3) as
significant. Given how much this table diverges, its result is best
read as suggestive at most, not a robust confirmation of the aid/oil
heterogeneity channel HR 2014 report.

**Reading the columns economically.** This table asks whether external
resource windfalls, over which a national government has discretion
but which did not have to be raised from its own citizens, are
disproportionately captured for political rather than developmental
use. Column (1)'s Leader $\times$ Aid interaction is the paper's aid-
fungibility result: foreign aid is meant to be spent on the purposes
donors attach to it, but if a marginal dollar of aid frees up an equal
dollar of the government's own revenue for other uses, aid becomes
fungible with general-purpose funds, and the authors' positive
interaction says that freed-up margin disproportionately reaches the
leader's own region rather than being spread nationally. Column (2)'s
Oil interaction is the natural comparison case, oil rents being a
domestic windfall rather than a donor transfer, and the authors'
near-zero, insignificant estimate there is consistent with oil revenue
being harder to redirect at the margin, whether because it is already
embedded in existing fiscal and budgetary institutions in a way project
aid is not, or because this project's own Oil measure is a coarser,
country-level proxy than the region-specific extraction data a cleaner
test would need. Columns (3)-(4) ask whether either channel is itself
conditional on institutional quality: a negative Aid $\times$ Polity
interaction says the aid-capture channel is weaker where political
constraints are stronger, the same institutional-brake story Table V's
Polity interaction tells for favoritism generally, extended here to
say that stronger institutions do not just reduce favoritism on
average, they specifically blunt a leader's ability to convert an aid
windfall into regional patronage.

```{r}
#| label: tbl-s5-aidoil
#| tbl-cap: "Table VII replication, HR 2014's aid/oil heterogeneity specification, in the main paper's Orig./Repl. layout and the authors' own row order (p. 1024). Standard errors in parentheses, clustered by leader spell."
#| tbl-pos: "H"

source("R/comparison_table_helpers.R")

m7 <- readRDS("../01_datasets/processed/ntl/table7_aid_oil_models.rds")
lb <- "fixest::l(is_birthregion)TRUE"
own_models <- list(m7$m1, m7$m2, m7$m3, m7$m4)

# HR 2014's own Table VII (p. 1024), transcribed directly.
hr_leader <- list(
    c(-0.019, 0.015, ""), c(0.020, 0.022, ""), c(0.086, 0.073, ""), c(0.118, 0.084, "")
)
hr_aid <- list(c(0.008, 0.002, "***"), NULL, c(0.019, 0.009, "**"), NULL)
hr_oil <- list(NULL, c(0.000, 0.002, ""), NULL, c(0.010, 0.008, ""))
hr_polity <- list(NULL, NULL, c(-0.121, 0.074, ""), c(-0.109, 0.094, ""))
hr_aid_polity <- list(NULL, NULL, c(-0.019, 0.010, "*"), NULL)
hr_oil_polity <- list(NULL, NULL, NULL, c(-0.014, 0.010, ""))

hr_n_regions <- c(38427, 38179, 38427, 37851)
hr_n_obs <- c(690495, 645396, 684213, 641410)
hr_r2 <- c(0.319, 0.335, 0.320, 0.335)

n_cols <- 4
row_leader <- c("Leader$_{t-1}$", as.vector(sapply(1:n_cols, function(i) {
    c(sstack_hr(hr_leader[[i]]), sstack_own(own_models[[i]], lb))
})))
row_aid <- c("Leader $\\times$ Aid$_{ct-1}$", as.vector(sapply(1:n_cols, function(i) {
    c(sstack_hr(hr_aid[[i]]), sstack_own(own_models[[i]], paste0(lb, ":fixest::l(aid)")))
})))
row_oil <- c("Leader $\\times$ Oil$_{ct-1}$", as.vector(sapply(1:n_cols, function(i) {
    c(sstack_hr(hr_oil[[i]]), sstack_own(own_models[[i]], paste0(lb, ":fixest::l(oil)")))
})))
row_polity <- c("Leader $\\times$ Polity$_{ct-1}$", as.vector(sapply(1:n_cols, function(i) {
    c(sstack_hr(hr_polity[[i]]), sstack_own(own_models[[i]], paste0(lb, ":fixest::l(polity)")))
})))
row_aid_polity <- c("Leader $\\times$ Aid$_{ct-1}$ $\\times$ Polity$_{ct-1}$", as.vector(sapply(1:n_cols, function(i) {
    c(sstack_hr(hr_aid_polity[[i]]), sstack_own(own_models[[i]], paste0(lb, ":fixest::l(aid):fixest::l(polity)")))
})))
row_oil_polity <- c("Leader $\\times$ Oil$_{ct-1}$ $\\times$ Polity$_{ct-1}$", as.vector(sapply(1:n_cols, function(i) {
    c(sstack_hr(hr_oil_polity[[i]]), sstack_own(own_models[[i]], paste0(lb, ":fixest::l(oil):fixest::l(polity)")))
})))

body <- rbind(row_leader, row_aid, row_oil, row_polity, row_aid_polity, row_oil_polity)
s7sum <- read.csv("../01_datasets/processed/ntl/table7_aid_oil_summary.csv")
foot <- rbind(
    c("Number of regions", as.vector(rbind(formatC(hr_n_regions, format = "d", big.mark = ","), formatC(s7sum$n_regions, format = "d", big.mark = ",")))),
    c("Observations", as.vector(rbind(formatC(hr_n_obs, format = "d", big.mark = ","), formatC(s7sum$n_obs, format = "d", big.mark = ",")))),
    c("$R^2$", as.vector(rbind(formatC(hr_r2, format = "f", digits = 3), formatC(s7sum$r2, format = "f", digits = 3)))),
    c("Region FE", as.vector(rbind("Yes", rep("Yes", n_cols)))),
    c("Country-Year FE", as.vector(rbind("Yes", rep("Yes", n_cols))))
)
out <- rbind(body, foot)
colnames(out) <- c("", rep(c("Orig.", "Repl."), n_cols))

render_comparison_table(
    out,
    n_cols = n_cols,
    col_headers = c("(1)", "(2)", "(3)", "(4)"),
    spanner_label = rep("Light$_{ict}$", n_cols),
    hline_before_foot = nrow(body),
    font_size = 8,
    notes = paste(
        "Fixed effect regressions using annual data for subnational regions between 1992 and 2009.",
        "Leader$_{ict-1}$ is a dummy variable equal to 1 if region $i$ is the birth region of the political leader in $t-1$, and 0 otherwise.",
        "Polity$_{ct-1}$ is the Polity2 score, rescaled so that it ranges from 0 to 1, with higher values implying stronger political institutions.",
        "Aid$_{ct-1}$ is the log of net overseas development assistance per capita plus 1.",
        "Oil$_{ct-1}$ is the log of oil rents per capita plus 1.",
        "Standard errors are adjusted for leader clustering.",
        "$^{***}$, $^{**}$, $^{*}$ indicate significance at the 1\\%, 5\\%, and 10\\% levels, respectively. (HR 2014, Table VII note, p. 1024, adapted.)",
        "This replication's own additions: Aid is built from QoG's OECD-DAC gross ODA series, IHS-transformed following Levy-Yeyati, Panizza and Stein (2007) as the authors specify; Oil is QoG's oil-rent series, log1p-transformed.",
        "Orig. $R^2$ is the authors' own reported $R^2$; Repl. reports fixest's overall (not within-transformed) $R^2$, which nets out the region and country-year fixed effects and is mechanically much closer to 1, so the two are not directly comparable in level."
    )
)
```

# Data and Code Availability {.unnumbered}

All data are drawn from open sources: subnational boundaries from GADM
[@gadm36], nighttime lights from DMSP-OLS [@noaa-dmsp], leader
identities and tenure from Archigos [@goemans2009], birthplaces from
PLAD [@plad2024] supplemented by a Wikidata scrape
[@wikidata-supplement], population from GPWv3 and GPWv4
[@ciesin-gpwv3; @ciesin-gpwv4], and the Table V/VI/VII covariates from
the Quality of Government dataset, the Penn World Table [@pwt71], the
Polity IV project [@marshall2010], Barro and Lee's schooling series
[@barrolee2013], Alesina et al.'s linguistic fractionalization
[@alesina2003], Alesina and Giuliano's family-ties measure
[@alesina2014], OECD development assistance statistics [@oecd-ids],
and the World Bank's adjusted net savings series [@wb-ans]. The
complete pipeline that builds every table in this document, and in the
main paper, is openly available in the replication repository
(<https://github.com/ofurkancoban/ofurkancoban-Regional_Favoritism_Replication>).
Table I, III, V, VI, and VII replicate five of the authors' seven
main-text tables that the main paper's page limit leaves no room for;
they are reported here in full rather than in the paper, and none of
them changes that paper's conclusions.

# Declaration of AI Use {.unnumbered}

During the preparation of this work, the author used Anthropic Claude
Sonnet 5 for coding assistance in building the
replication pipeline and for English-language improvement of the
manuscript text. After using this tool, the author reviewed and edited
the content as needed and takes full responsibility for the content of
this publication.

# References {.unnumbered}

```{=latex}
\begin{multicols}{2}
\small
```

::: {#refs}
:::

```{=latex}
\end{multicols}
```
